---
title: "Customer & Revenue Analysis"
subtitle: "Order Economics, Customer Segmentation, and Growth Opportunity"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
    fig_width: 10
    fig_height: 6
    css: !expr NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE,
  fig.align = "center", out.width = "100%"
)

library(dplyr)
library(ggplot2)
library(readr)
library(stringr)
library(tidyr)
library(lubridate)
library(scales)
library(gridExtra)
library(knitr)
if (!requireNamespace("zoo", quietly = TRUE)) install.packages("zoo", quiet = TRUE)
library(zoo)
```

```{r load-data}
bc_orders <- read_csv("orders-2026-03-25.csv", show_col_types = FALSE)
zoho_contacts <- read_csv("Contacts_2026_03_25.csv", show_col_types = FALSE)
zoho_accounts <- read_csv("Accounts_2025_03_25.csv", show_col_types = FALSE)
bc_customers <- read_csv("BC_customers.csv", show_col_types = FALSE)
stripe_customers <- read_csv("stripe_unified_customers.csv", show_col_types = FALSE)
```

```{r prep-bigcommerce}
bc_clean <- bc_orders %>%
  mutate(
    order_date = mdy(`Order Date`),
    order_year = year(order_date),
    order_total = as.numeric(gsub("[^0-9.]", "", `Order Total (inc tax)`)),
    customer_email = tolower(trimws(`Customer Email`)),
    billing_email = tolower(trimws(`Billing Email`)),
    shipping_company = tolower(trimws(`Shipping Company`)),
    billing_company = tolower(trimws(`Billing Company`)),
    customer_group = tolower(trimws(`Customer Group Name`)),
    customer_name = trimws(`Customer Name`),
    billing_name = trimws(`Billing Name`),
    shipping_name = trimws(`Shipping Name`)
  ) %>%
  filter(order_year %in% c(2023, 2024, 2025)) %>%
  mutate(
    match_email = case_when(
      !is.na(customer_email) & customer_email != "" ~ customer_email,
      !is.na(billing_email) & billing_email != ""   ~ billing_email,
      TRUE ~ NA_character_
    )
  )
```

```{r prep-zoho}
zoho_clean <- zoho_contacts %>%
  mutate(
    zoho_email = tolower(trimws(Email)),
    zoho_customer_type = tolower(trimws(`Customer Type`)),
    zoho_business_type = tolower(trimws(`Business Type`)),
    zoho_contact_type = tolower(trimws(`Contact Type`)),
    zoho_lead_source = tolower(trimws(`Lead Source`)),
    zoho_trade_status = tolower(trimws(`Trade Program Status`)),
    zoho_trade_interest = tolower(trimws(`Trade Program Interest`)),
    zoho_trade_program = tolower(trimws(`Trade Program`)),
    zoho_professional_type = tolower(trimws(ifelse(
      "professionalType" %in% names(.), `professionalType`, NA_character_
    ))),
    zoho_customer_type_meta = tolower(trimws(ifelse(
      "customerType" %in% names(.), `customerType`, NA_character_
    ))),
    zoho_trade_interest_meta = tolower(trimws(ifelse(
      "tradeProgramInterest" %in% names(.), `tradeProgramInterest`, NA_character_
    ))),
    zoho_pro_project_type = tolower(trimws(ifelse(
      "proProjectType" %in% names(.), `proProjectType`, NA_character_
    ))),
    zoho_projects_per_year = tolower(trimws(`Projects per Year`)),
    zoho_disaster_recovery = tolower(trimws(`Disaster Recovery?`)),
    zoho_business_id = trimws(`Business ID`),
    zoho_business_entity = trimws(`Business Entity`),
    zoho_tax_exempt = tolower(trimws(`Tax Exempt?`)),
    zoho_company = tolower(trimws(`Account Name`)),
    zoho_first_name = trimws(`First Name`),
    zoho_last_name = trimws(`Last Name`),
    zoho_full_name = trimws(paste(zoho_first_name, zoho_last_name))
  )
```

```{r classify-zoho}
personal_email_domains <- c(
  "gmail.com", "yahoo.com", "hotmail.com", "outlook.com", "aol.com",
  "icloud.com", "me.com", "mac.com", "live.com", "msn.com",
  "comcast.net", "att.net", "verizon.net", "sbcglobal.net", "cox.net",
  "charter.net", "earthlink.net", "optonline.net", "frontier.com",
  "windstream.net", "centurylink.net", "embarqmail.com", "suddenlink.net",
  "mail.com", "email.com", "ymail.com", "rocketmail.com", "protonmail.com",
  "zoho.com", "fastmail.com", "hushmail.com", "inbox.com", "gmx.com"
)

company_junk <- c(
  "", "n/a", "na", "none", "no", "self", "retired", "home", "homeowner",
  "yes", "kitchen", "bath", "bathroom", "bathroom remodel", "cabinet doors",
  "stock cabinets", "custom cabinets", "cabinets", "google", "bigcommerce",
  "reflectiz bigcommerce", "facebook", "instagram"
)

zoho_classified <- zoho_clean %>%
  mutate(
    email_domain = str_extract(zoho_email, "(?<=@)[^@]+$"),
    has_business_email = !is.na(email_domain) & !(email_domain %in% personal_email_domains),
    sig_customer_type = zoho_customer_type %in% c(
      "professional", "commercial", "contractor", "builder", "designer",
      "architect", "trade", "dealer", "wholesale", "business"
    ),
    sig_business_type = !is.na(zoho_business_type) & zoho_business_type != "" &
      zoho_business_type != "homeowner" & zoho_business_type != "residential",
    sig_contact_type = zoho_contact_type %in% c(
      "professional", "commercial", "contractor", "trade", "dealer", "business"
    ),
    sig_trade_status = !is.na(zoho_trade_status) & zoho_trade_status != "" &
      zoho_trade_status != "none" & zoho_trade_status != "n/a",
    sig_trade_interest = !is.na(zoho_trade_interest) & zoho_trade_interest != "" &
      zoho_trade_interest != "no" & zoho_trade_interest != "none" &
      zoho_trade_interest != "n/a",
    sig_trade_program = !is.na(zoho_trade_program) & zoho_trade_program == "true",
    sig_professional_type = !is.na(zoho_professional_type) &
      zoho_professional_type != "" & zoho_professional_type != "homeowner",
    sig_business_id = !is.na(zoho_business_id) & zoho_business_id != "",
    sig_business_entity = !is.na(zoho_business_entity) & zoho_business_entity != "",
    sig_tax_exempt = !is.na(zoho_tax_exempt) & zoho_tax_exempt != "",
    sig_customer_type_meta = !is.na(zoho_customer_type_meta) &
      zoho_customer_type_meta %in% c("professional", "both"),
    sig_trade_interest_meta = !is.na(zoho_trade_interest_meta) &
      zoho_trade_interest_meta != "",
    sig_pro_project_type = !is.na(zoho_pro_project_type) & zoho_pro_project_type != "",
    sig_projects_per_year = !is.na(zoho_projects_per_year) & zoho_projects_per_year != "",
    sig_disaster_recovery = !is.na(zoho_disaster_recovery) &
      zoho_disaster_recovery != "" & zoho_disaster_recovery != "no",
    sig_company_raw = !is.na(zoho_company) &
      !(zoho_company %in% company_junk) &
      !(zoho_company == tolower(paste(zoho_first_name, zoho_last_name))) &
      !(zoho_company == tolower(zoho_last_name)),
    sig_email_raw = has_business_email,
    sig_residential = (zoho_customer_type %in% c("homeowner", "residential") |
      zoho_business_type %in% c("homeowner", "residential") |
      zoho_contact_type %in% c("homeowner", "residential") |
      zoho_customer_type_meta == "homeowner"),
    strong_signal_count = sig_customer_type + sig_business_type + sig_contact_type +
      sig_trade_status + sig_trade_interest + sig_trade_program +
      sig_professional_type + sig_business_id + sig_business_entity +
      sig_tax_exempt + sig_customer_type_meta + sig_trade_interest_meta +
      sig_pro_project_type + sig_projects_per_year + sig_disaster_recovery,
    weak_signal_count = sig_company_raw + sig_email_raw,
    pro_signal_count = strong_signal_count + weak_signal_count,
    is_professional = (strong_signal_count >= 1) | (weak_signal_count >= 2),
    customer_class = case_when(
      is_professional & !sig_residential ~ "Professional",
      is_professional & sig_residential  ~ "Professional",
      sig_residential                    ~ "Residential",
      TRUE                               ~ "Unknown"
    ),
    classification_confidence = case_when(
      strong_signal_count >= 2 ~ "High",
      strong_signal_count == 1 ~ "Medium",
      weak_signal_count >= 2   ~ "Low",
      sig_residential          ~ "Medium",
      TRUE                     ~ "No Signal"
    )
  )

# One row per email for lookups
zoho_lookup <- zoho_classified %>%
  filter(!is.na(zoho_email) & zoho_email != "") %>%
  group_by(zoho_email) %>%
  slice_max(pro_signal_count, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  select(zoho_email, customer_class, classification_confidence, pro_signal_count,
         zoho_company, zoho_customer_type, zoho_business_type, zoho_trade_status,
         starts_with("sig_"))
```

```{r accounts-and-address-signals}
# Zoho Accounts: additional classification source
acct_classified <- zoho_accounts %>%
  mutate(
    acct_email = tolower(trimws(ifelse("Email 1" %in% names(.), `Email 1`, NA_character_))),
    acct_customer_type = tolower(trimws(`Customer Type`)),
    acct_business_type = tolower(trimws(`Business Type`)),
    acct_contact_type = tolower(trimws(`Contact Type`)),
    acct_trade_interest = tolower(trimws(`Trade Program Interest`)),
    acct_trade_program = tolower(trimws(`Trade Program`)),
    acct_projects_per_year = tolower(trimws(`Projects per Year`)),
    acct_disaster_recovery = tolower(trimws(`Disaster Recovery?`)),
    acct_account_type = tolower(trimws(`Account Type`)),
    acct_industry = tolower(trimws(Industry))
  ) %>%
  mutate(
    acct_is_pro = acct_customer_type %in% c("professional","commercial","contractor","builder",
      "designer","architect","trade","dealer","wholesale","business") |
      (!is.na(acct_business_type) & acct_business_type != "" &
       !acct_business_type %in% c("homeowner","residential")) |
      acct_contact_type %in% c("professional","commercial","contractor","trade","dealer","business") |
      (!is.na(acct_trade_interest) & acct_trade_interest != "" &
       !acct_trade_interest %in% c("no","none","n/a")) |
      (!is.na(acct_trade_program) & acct_trade_program == "true") |
      (!is.na(acct_projects_per_year) & acct_projects_per_year != "") |
      (!is.na(acct_disaster_recovery) & acct_disaster_recovery != "" & acct_disaster_recovery != "no") |
      (!is.na(acct_industry) & acct_industry != "") |
      (!is.na(acct_account_type) & acct_account_type != "" &
       !acct_account_type %in% c("customer","other",""))
  )

acct_lookup <- acct_classified %>%
  filter(!is.na(acct_email) & acct_email != "" & acct_is_pro) %>%
  distinct(acct_email) %>% mutate(acct_is_professional = TRUE)

# BigCommerce: different shipping vs billing name+address = professional
bc_address_signal <- bc_clean %>%
  filter(!is.na(match_email)) %>%
  mutate(
    ship_name = tolower(trimws(`Shipping Name`)),
    bill_name = tolower(trimws(`Billing Name`)),
    ship_addr = tolower(trimws(paste(`Shipping Street 1`, `Shipping Suburb`,
                                      `Shipping State`, `Shipping Zip`))),
    bill_addr = tolower(trimws(paste(`Billing Street 1`, `Billing Suburb`,
                                      `Billing State`, `Billing Zip`))),
    diff_name_and_addr = !is.na(ship_name) & !is.na(bill_name) & ship_name != "" &
      bill_name != "" & ship_name != bill_name &
      !is.na(ship_addr) & !is.na(bill_addr) & ship_addr != bill_addr
  ) %>%
  group_by(match_email) %>%
  summarise(has_diff_ship_bill = any(diff_name_and_addr, na.rm = TRUE), .groups = "drop") %>%
  filter(has_diff_ship_bill)

# BC Customers file: Company field = professional
bc_cust_lookup <- bc_customers %>%
  mutate(bc_cust_email = tolower(trimws(Email)),
         bc_cust_company = tolower(trimws(Company))) %>%
  filter(!is.na(bc_cust_email) & bc_cust_email != "") %>%
  mutate(bc_cust_has_company = !is.na(bc_cust_company) & bc_cust_company != "" &
    !bc_cust_company %in% c("n/a","na","none","-","self","home","retired")) %>%
  filter(bc_cust_has_company) %>%
  distinct(bc_cust_email) %>% mutate(bc_cust_is_pro = TRUE)

# Business name keywords pattern
biz_keywords <- c(
  "cabinetry","cabinets","cabinet","painting","painters","paint",
  "handyman","design","designs","designer","designing",
  "homes","home builder","homebuilder","builders","building",
  "construction","contracting","contractor","contractors",
  "remodel","remodeling","remodelers","renovation","renovations",
  "woodwork","woodworking","millwork","carpentry","carpenter",
  "plumbing","plumber","electric","electrical","electrician",
  "roofing","roofer","flooring","tile","tiling",
  "restoration","restorations","maintenance",
  "property","properties","real estate","realty",
  "interiors","interior","staging","decor",
  "kitchen","kitchens","bath",
  "llc","inc","corp","co\\.","& sons","& son",
  "enterprises","services","solutions","group","associates",
  "custom","pro ","professional"
)
biz_pattern <- paste(biz_keywords, collapse = "|")
```

```{r stripe-master}
# ==========================================================================
# STRIPE AS AUTHORITY: Build the master customer list from Stripe
# ==========================================================================

stripe_clean <- stripe_customers %>%
  mutate(
    stripe_email = tolower(trimws(Email)),
    stripe_name = trimws(Name),
    stripe_total_spend = as.numeric(gsub("[^0-9.]", "", `Total Spend`)),
    stripe_payment_count = as.numeric(`Payment Count`),
    stripe_avg_order = as.numeric(gsub("[^0-9.]", "", `Average Order`)),
    stripe_refunded = as.numeric(gsub("[^0-9.]", "", `Refunded Volume`)),
    stripe_created = ymd_hms(`Created (UTC)`, quiet = TRUE)
  ) %>%
  filter(!is.na(stripe_email) & stripe_email != "")

# Consolidate to one row per email (Stripe can have duplicates)
stripe_deduped <- stripe_clean %>%
  group_by(stripe_email) %>%
  summarise(
    stripe_name = first(na.omit(stripe_name)),
    total_spend = sum(stripe_total_spend, na.rm = TRUE),
    total_orders = sum(stripe_payment_count, na.rm = TRUE),
    avg_order = ifelse(sum(stripe_payment_count, na.rm = TRUE) > 0,
                       sum(stripe_total_spend, na.rm = TRUE) / sum(stripe_payment_count, na.rm = TRUE),
                       0),
    total_refunded = sum(stripe_refunded, na.rm = TRUE),
    first_seen = min(stripe_created, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  filter(total_spend > 0) %>%
  mutate(first_year = year(first_seen))

# Filter to customers active in 2023-2025
bc_active_emails <- bc_clean %>%
  filter(!is.na(match_email)) %>% distinct(match_email) %>% pull()

customer_master <- stripe_deduped %>%
  filter(
    first_year >= 2023 |                   # Created during period
    stripe_email %in% bc_active_emails     # Has BC order in 2023-2025
  )

# Classify from Zoho — email match first
customer_master <- customer_master %>%
  left_join(zoho_lookup %>% select(zoho_email, customer_class, classification_confidence,
                                    pro_signal_count),
            by = c("stripe_email" = "zoho_email"))

# Name-based fallback for unmatched
zoho_name_lookup <- zoho_classified %>%
  filter(!is.na(zoho_full_name) & zoho_full_name != "" &
         zoho_full_name != "NA NA" & nchar(zoho_full_name) > 3) %>%
  mutate(match_name = tolower(zoho_full_name)) %>%
  group_by(match_name) %>%
  slice_max(pro_signal_count, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  add_count(match_name, name = "name_freq") %>%
  filter(name_freq == 1) %>%
  select(match_name, name_customer_class = customer_class,
         name_confidence = classification_confidence,
         name_signal_count = pro_signal_count)

customer_master <- customer_master %>%
  mutate(stripe_match_name = tolower(trimws(stripe_name)))

name_join <- customer_master %>%
  filter(is.na(customer_class) & !is.na(stripe_match_name) & stripe_match_name != "") %>%
  select(stripe_email, stripe_match_name) %>%
  inner_join(zoho_name_lookup, by = c("stripe_match_name" = "match_name"))

customer_master <- customer_master %>%
  left_join(name_join %>% select(stripe_email, name_customer_class, name_confidence, name_signal_count),
            by = "stripe_email") %>%
  mutate(
    customer_class = ifelse(is.na(customer_class), name_customer_class, customer_class),
    classification_confidence = ifelse(is.na(classification_confidence), name_confidence, classification_confidence),
    pro_signal_count = ifelse(is.na(pro_signal_count), name_signal_count, pro_signal_count)
  ) %>%
  select(-name_customer_class, -name_confidence, -name_signal_count)

# BC name-based pro signals
bc_name_lookup <- bc_clean %>%
  filter(!is.na(customer_name) & customer_name != "") %>%
  mutate(match_name = tolower(trimws(customer_name))) %>%
  group_by(match_name) %>%
  summarise(
    bc_shipping_company_name = first(na.omit(shipping_company)),
    bc_billing_company_name = first(na.omit(billing_company)),
    bc_customer_group_name = first(na.omit(customer_group)), .groups = "drop"
  ) %>%
  add_count(match_name, name = "name_freq") %>%
  filter(name_freq == 1) %>%
  mutate(
    bc_name_is_pro = (!is.na(bc_shipping_company_name) & bc_shipping_company_name != "" &
      !bc_shipping_company_name %in% c("n/a","na","none","-")) |
      (!is.na(bc_billing_company_name) & bc_billing_company_name != "" &
      !bc_billing_company_name %in% c("n/a","na","none","-")) |
      bc_customer_group_name %in% c("professional","commercial","trade","wholesale",
        "dealer","contractor","builder","business")
  ) %>%
  filter(bc_name_is_pro) %>%
  select(match_name, bc_name_is_pro)

# Enrich from BigCommerce
bc_company_lookup <- bc_clean %>%
  filter(!is.na(match_email)) %>%
  group_by(match_email) %>%
  summarise(
    bc_shipping_company = first(na.omit(shipping_company)),
    bc_billing_company = first(na.omit(billing_company)),
    bc_customer_group = first(na.omit(customer_group)),
    bc_customer_name = first(na.omit(customer_name)),
    .groups = "drop"
  ) %>%
  mutate(
    bc_has_shipping_co = !is.na(bc_shipping_company) & bc_shipping_company != "" &
      !bc_shipping_company %in% c("n/a", "na", "none", "-"),
    bc_has_billing_co = !is.na(bc_billing_company) & bc_billing_company != "" &
      !bc_billing_company %in% c("n/a", "na", "none", "-"),
    bc_has_company = bc_has_shipping_co | bc_has_billing_co,
    bc_group_pro = bc_customer_group %in% c(
      "professional", "commercial", "trade", "wholesale", "dealer",
      "contractor", "contractors", "builder", "business",
      "trade program - level 1"
    ),
    bc_name_has_biz = !is.na(bc_customer_name) &
      grepl(biz_pattern, tolower(bc_customer_name), ignore.case = TRUE)
  )

stripe_name_has_biz <- customer_master %>%
  filter(!is.na(stripe_match_name) & stripe_match_name != "") %>%
  mutate(has_biz = grepl(biz_pattern, stripe_match_name, ignore.case = TRUE)) %>%
  filter(has_biz) %>% distinct(stripe_email) %>%
  mutate(stripe_name_is_biz = TRUE)

customer_master <- customer_master %>%
  left_join(bc_company_lookup, by = c("stripe_email" = "match_email")) %>%
  left_join(acct_lookup, by = c("stripe_email" = "acct_email")) %>%
  left_join(bc_address_signal, by = c("stripe_email" = "match_email")) %>%
  left_join(bc_name_lookup, by = c("stripe_match_name" = "match_name")) %>%
  left_join(bc_cust_lookup, by = c("stripe_email" = "bc_cust_email")) %>%
  left_join(stripe_name_has_biz, by = "stripe_email") %>%
  mutate(
    acct_is_professional = ifelse(is.na(acct_is_professional), FALSE, acct_is_professional),
    has_diff_ship_bill = ifelse(is.na(has_diff_ship_bill), FALSE, has_diff_ship_bill),
    bc_name_is_pro = ifelse(is.na(bc_name_is_pro), FALSE, bc_name_is_pro),
    bc_cust_is_pro = ifelse(is.na(bc_cust_is_pro), FALSE, bc_cust_is_pro),
    bc_name_has_biz = ifelse(is.na(bc_name_has_biz), FALSE, bc_name_has_biz),
    stripe_name_is_biz = ifelse(is.na(stripe_name_is_biz), FALSE, stripe_name_is_biz),
    # Professional always wins
    final_class = case_when(
      customer_class == "Professional"       ~ "Professional",
      acct_is_professional                   ~ "Professional",
      bc_has_company | bc_group_pro          ~ "Professional",
      bc_cust_is_pro                         ~ "Professional",
      bc_name_is_pro                         ~ "Professional",
      bc_name_has_biz                        ~ "Professional",
      stripe_name_is_biz                     ~ "Professional",
      has_diff_ship_bill                     ~ "Professional",
      customer_class == "Residential"        ~ "Residential",
      TRUE                                   ~ "Unknown"
    ),
    display_class = case_when(
      final_class == "Professional" ~ "Professional",
      final_class == "Residential"  ~ "Residential",
      TRUE                          ~ "Residential (assumed)"
    ),
    broad_class = ifelse(final_class == "Professional", "Professional", "Residential"),
    is_repeat = total_orders > 1
  )
```

```{r bc-yearly-data}
# BigCommerce order-level data for yearly trend analysis
orders_merged <- bc_clean %>%
  mutate(bc_match_name = tolower(trimws(customer_name))) %>%
  left_join(zoho_lookup %>% select(zoho_email, customer_class),
            by = c("match_email" = "zoho_email")) %>%
  left_join(zoho_name_lookup %>% select(match_name, name_customer_class),
            by = c("bc_match_name" = "match_name")) %>%
  mutate(customer_class = ifelse(is.na(customer_class), name_customer_class, customer_class)) %>%
  select(-name_customer_class) %>%
  left_join(bc_company_lookup %>% select(match_email, bc_has_company, bc_group_pro, bc_name_has_biz),
            by = c("match_email" = "match_email")) %>%
  left_join(acct_lookup, by = c("match_email" = "acct_email")) %>%
  left_join(bc_address_signal, by = c("match_email" = "match_email")) %>%
  left_join(bc_name_lookup, by = c("bc_match_name" = "match_name")) %>%
  left_join(bc_cust_lookup, by = c("match_email" = "bc_cust_email")) %>%
  mutate(
    acct_is_professional = ifelse(is.na(acct_is_professional), FALSE, acct_is_professional),
    has_diff_ship_bill = ifelse(is.na(has_diff_ship_bill), FALSE, has_diff_ship_bill),
    bc_name_is_pro = ifelse(is.na(bc_name_is_pro), FALSE, bc_name_is_pro),
    bc_cust_is_pro = ifelse(is.na(bc_cust_is_pro), FALSE, bc_cust_is_pro),
    bc_name_has_biz = ifelse(is.na(bc_name_has_biz), FALSE, bc_name_has_biz),
    # Professional always wins
    final_class = case_when(
      customer_class == "Professional"       ~ "Professional",
      acct_is_professional                   ~ "Professional",
      bc_has_company | bc_group_pro          ~ "Professional",
      bc_cust_is_pro                         ~ "Professional",
      bc_name_is_pro                         ~ "Professional",
      bc_name_has_biz                        ~ "Professional",
      has_diff_ship_bill                     ~ "Professional",
      customer_class == "Residential"        ~ "Residential",
      TRUE                                   ~ "Unknown"
    ),
    display_class = case_when(
      final_class == "Professional" ~ "Professional",
      final_class == "Residential"  ~ "Residential",
      TRUE                          ~ "Residential (assumed)"
    ),
    broad_class = ifelse(final_class == "Professional", "Professional", "Residential")
  )

# Yearly summary from BC (for trend charts)
yearly_summary <- orders_merged %>%
  group_by(order_year, broad_class) %>%
  summarise(
    order_count = n(),
    total_revenue = sum(order_total, na.rm = TRUE),
    avg_order_size = mean(order_total, na.rm = TRUE),
    median_order_size = median(order_total, na.rm = TRUE),
    unique_customers = n_distinct(match_email, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  group_by(order_year) %>%
  mutate(
    pct_orders = round(order_count / sum(order_count) * 100, 1),
    pct_revenue = round(total_revenue / sum(total_revenue) * 100, 1)
  ) %>%
  ungroup()

# Repeat by year from BC
repeat_by_year <- orders_merged %>%
  filter(!is.na(match_email)) %>%
  arrange(match_email, order_date) %>%
  group_by(match_email) %>%
  mutate(cumulative_order_num = row_number(), is_repeat_order = cumulative_order_num > 1) %>%
  ungroup() %>%
  group_by(order_year, broad_class) %>%
  summarise(total_orders = n(), repeat_orders = sum(is_repeat_order),
            repeat_order_rate = round(repeat_orders / total_orders * 100, 1),
            .groups = "drop")
```

```{r compute-summaries}
# --- Stripe-authoritative totals ---
total_customers <- nrow(customer_master)
total_revenue <- sum(customer_master$total_spend, na.rm = TRUE)
total_orders <- sum(customer_master$total_orders, na.rm = TRUE)
no_signal_pct <- round(sum(customer_master$final_class == "Unknown") / total_customers * 100, 1)

# Summary by type (from Stripe)
type_summary <- customer_master %>%
  group_by(broad_class) %>%
  summarise(
    customers = n(),
    revenue = sum(total_spend, na.rm = TRUE),
    orders = sum(total_orders, na.rm = TRUE),
    avg_order = round(sum(total_spend, na.rm = TRUE) / sum(total_orders, na.rm = TRUE), 2),
    avg_ltv = round(mean(total_spend, na.rm = TRUE), 2),
    median_ltv = round(median(total_spend, na.rm = TRUE), 2),
    repeat_customers = sum(is_repeat),
    repeat_rate = round(sum(is_repeat) / n() * 100, 1),
    avg_orders_per_cust = round(mean(total_orders, na.rm = TRUE), 2),
    .groups = "drop"
  ) %>%
  mutate(
    pct_customers = round(customers / sum(customers) * 100, 1),
    pct_revenue = round(revenue / sum(revenue) * 100, 1),
    pct_orders = round(orders / sum(orders) * 100, 1)
  )

# Certainty from Stripe master
certainty_stripe <- customer_master %>%
  count(display_class) %>%
  mutate(pct = round(n / sum(n) * 100, 1))
```

```{r theme-setup}
theme_buyer <- theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", size = 15),
    plot.subtitle = element_text(color = "gray40", size = 11),
    legend.position = "bottom",
    panel.grid.minor = element_blank()
  )

colors_class <- c("Professional" = "#2C5F8A", "Residential" = "#E8894A")
colors_detail <- c("Professional" = "#2C5F8A", "Residential" = "#E8894A",
                    "Residential (assumed)" = "#F5C285")
```

# Executive Summary

This report analyzes **`r comma(total_customers)`** paying customers representing **`r dollar(total_revenue)`** in total revenue across **`r comma(total_orders)`** orders. Revenue and customer counts are sourced from **Stripe** (authoritative payment system). Customer classification uses signals from **Zoho CRM** and **BigCommerce**.

```{r exec-summary-table}
exec_tbl <- type_summary %>%
  transmute(
    `Customer Type` = broad_class,
    Customers = comma(customers),
    `% Customers` = paste0(pct_customers, "%"),
    Orders = comma(orders),
    `% Orders` = paste0(pct_orders, "%"),
    Revenue = dollar(revenue),
    `% Revenue` = paste0(pct_revenue, "%"),
    `Avg Order` = dollar(avg_order),
    `Avg LTV` = dollar(avg_ltv)
  )

kable(exec_tbl, align = "lrrrrrrrr")
```

> **Classification certainty:** `r no_signal_pct`% of customers had no signal indicating either type and are assumed Residential. These are tracked separately in the confidence section below.

---

# Customer Composition {.tabset}

## By Customer Count

```{r plot-cust-count, fig.height=5, fig.width=8}
type_summary %>%
  ggplot(aes(x = broad_class, y = customers, fill = broad_class)) +
  geom_col(width = 0.5) +
  geom_text(aes(label = paste0(comma(customers), "\n(", pct_customers, "%)")),
            vjust = -0.3, size = 4.5, fontface = "bold") +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = comma, expand = expansion(mult = c(0, 0.2))) +
  labs(x = "", y = "Customers", fill = "Customer Type",
       title = "Customers by Type",
       subtitle = "Based on Stripe payment records (paying customers only)") +
  theme_buyer
```

## By Revenue

```{r plot-rev-split, fig.height=5, fig.width=8}
type_summary %>%
  ggplot(aes(x = broad_class, y = revenue, fill = broad_class)) +
  geom_col(width = 0.5) +
  geom_text(aes(label = paste0(dollar(revenue, accuracy = 1), "\n(", pct_revenue, "%)")),
            vjust = -0.3, size = 4.5, fontface = "bold") +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = dollar, expand = expansion(mult = c(0, 0.2))) +
  labs(x = "", y = "Revenue", fill = "Customer Type",
       title = "Revenue by Customer Type",
       subtitle = "Total lifetime revenue from Stripe") +
  theme_buyer
```

## By Order Count

```{r plot-order-split, fig.height=5, fig.width=8}
type_summary %>%
  ggplot(aes(x = broad_class, y = orders, fill = broad_class)) +
  geom_col(width = 0.5) +
  geom_text(aes(label = paste0(comma(orders), "\n(", pct_orders, "%)")),
            vjust = -0.3, size = 4.5, fontface = "bold") +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = comma, expand = expansion(mult = c(0, 0.2))) +
  labs(x = "", y = "Orders", fill = "Customer Type",
       title = "Orders by Customer Type",
       subtitle = "Total order count from Stripe") +
  theme_buyer
```

# Average Order Size & Customer LTV

```{r plot-avg-ltv, fig.height=5}
ltv_data <- type_summary %>%
  select(broad_class, `Avg Order Size` = avg_order, `Avg Customer LTV` = avg_ltv,
         `Median Customer LTV` = median_ltv) %>%
  pivot_longer(-broad_class, names_to = "metric", values_to = "value") %>%
  mutate(metric = factor(metric, levels = c("Avg Order Size", "Avg Customer LTV", "Median Customer LTV")))

ltv_data %>%
  ggplot(aes(x = metric, y = value, fill = broad_class)) +
  geom_col(position = "dodge", width = 0.7) +
  geom_text(aes(label = dollar(value, accuracy = 1)),
            position = position_dodge(width = 0.7), vjust = -0.5, size = 4) +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = dollar, expand = expansion(mult = c(0, 0.15))) +
  labs(x = "", y = "", fill = "Customer Type",
       title = "Order Size & Lifetime Value by Customer Type",
       subtitle = "From Stripe payment data") +
  theme_buyer
```

# Repeat Customer Behavior

```{r plot-repeat, fig.height=5}
repeat_data <- type_summary %>%
  select(broad_class, repeat_rate, avg_orders_per_cust) %>%
  pivot_longer(-broad_class, names_to = "metric", values_to = "value") %>%
  mutate(metric = recode(metric,
    "repeat_rate" = "Repeat Rate (%)",
    "avg_orders_per_cust" = "Avg Orders per Customer"
  ))

gridExtra::grid.arrange(
  # Repeat rate
  type_summary %>%
    ggplot(aes(x = broad_class, y = repeat_rate, fill = broad_class)) +
    geom_col(width = 0.5) +
    geom_text(aes(label = paste0(repeat_rate, "%")), vjust = -0.5, size = 5, fontface = "bold") +
    scale_fill_manual(values = colors_class) +
    scale_y_continuous(labels = function(x) paste0(x, "%"), expand = expansion(mult = c(0, 0.2))) +
    labs(x = "", y = "Repeat Rate", fill = "Customer Type",
         title = "Repeat Customer Rate", subtitle = "Customers with 2+ orders") +
    theme_buyer,

  # Avg orders per customer
  type_summary %>%
    ggplot(aes(x = broad_class, y = avg_orders_per_cust, fill = broad_class)) +
    geom_col(width = 0.5) +
    geom_text(aes(label = sprintf("%.1f", avg_orders_per_cust)), vjust = -0.5, size = 5, fontface = "bold") +
    scale_fill_manual(values = colors_class) +
    scale_y_continuous(expand = expansion(mult = c(0, 0.2))) +
    labs(x = "", y = "Avg Orders", fill = "Customer Type",
         title = "Orders per Customer", subtitle = "Average from Stripe") +
    theme_buyer,

  ncol = 2
)
```

```{r repeat-table}
repeat_tbl <- type_summary %>%
  transmute(
    Type = broad_class,
    Customers = comma(customers),
    `Repeat Customers` = comma(repeat_customers),
    `Repeat Rate` = paste0(repeat_rate, "%"),
    `Avg Orders/Customer` = avg_orders_per_cust,
    `Avg LTV` = dollar(avg_ltv),
    `Median LTV` = dollar(median_ltv)
  )

kable(repeat_tbl, align = "lrrrrrr")
```

# Year-over-Year Trends

*Note: Yearly breakdowns use BigCommerce order data, which captures a subset of total Stripe transactions. These charts show directional trends rather than absolute totals.*

## Order Volume by Year

```{r plot-yearly-orders, fig.height=5}
yearly_summary %>%
  ggplot(aes(x = factor(order_year), y = order_count, fill = broad_class)) +
  geom_col(position = "dodge", width = 0.7) +
  geom_text(aes(label = comma(order_count)),
            position = position_dodge(width = 0.7), vjust = -0.5, size = 4) +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = comma, expand = expansion(mult = c(0, 0.15))) +
  labs(x = "Year", y = "Order Count", fill = "Customer Type",
       title = "Orders by Customer Type and Year",
       subtitle = "Source: BigCommerce (partial coverage)") +
  theme_buyer
```

## Revenue by Year

```{r plot-yearly-revenue, fig.height=5}
yearly_summary %>%
  ggplot(aes(x = factor(order_year), y = total_revenue, fill = broad_class)) +
  geom_col(position = "dodge", width = 0.7) +
  geom_text(aes(label = dollar(total_revenue, accuracy = 1)),
            position = position_dodge(width = 0.7), vjust = -0.5, size = 3.5) +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = dollar, expand = expansion(mult = c(0, 0.15))) +
  labs(x = "Year", y = "Revenue", fill = "Customer Type",
       title = "Revenue by Customer Type and Year",
       subtitle = "Source: BigCommerce (partial coverage)") +
  theme_buyer
```

## Revenue Share by Year

```{r plot-yearly-share, fig.height=5}
yearly_summary %>%
  ggplot(aes(x = factor(order_year), y = pct_revenue, fill = broad_class)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = paste0(pct_revenue, "%")),
            position = position_stack(vjust = 0.5), size = 5, color = "white",
            fontface = "bold") +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = function(x) paste0(x, "%")) +
  labs(x = "Year", y = "% of Revenue", fill = "Customer Type",
       title = "Revenue Share by Customer Type",
       subtitle = "Source: BigCommerce (partial coverage)") +
  theme_buyer
```

## Average Order Size by Year

```{r plot-yearly-avg, fig.height=5}
yearly_summary %>%
  ggplot(aes(x = factor(order_year), y = avg_order_size, fill = broad_class)) +
  geom_col(position = "dodge", width = 0.7) +
  geom_text(aes(label = dollar(avg_order_size, accuracy = 1)),
            position = position_dodge(width = 0.7), vjust = -0.5, size = 4) +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = dollar, expand = expansion(mult = c(0, 0.15))) +
  labs(x = "Year", y = "Avg Order Size", fill = "Customer Type",
       title = "Average Order Size by Year",
       subtitle = "Source: BigCommerce (partial coverage)") +
  theme_buyer
```

## Repeat Order Rate by Year

```{r plot-yearly-repeat, fig.height=5}
repeat_by_year %>%
  ggplot(aes(x = factor(order_year), y = repeat_order_rate, fill = broad_class)) +
  geom_col(position = "dodge", width = 0.7) +
  geom_text(aes(label = paste0(repeat_order_rate, "%")),
            position = position_dodge(width = 0.7), vjust = -0.5, size = 4) +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = function(x) paste0(x, "%"),
                     expand = expansion(mult = c(0, 0.15))) +
  labs(x = "Year", y = "Repeat Order %", fill = "Customer Type",
       title = "Repeat Order Rate by Year",
       subtitle = "% of orders from returning customers (BigCommerce data)") +
  theme_buyer
```

```{r yearly-detail-table}
yearly_tbl <- yearly_summary %>%
  transmute(
    Year = order_year, Type = broad_class,
    Orders = comma(order_count), `% Orders` = paste0(pct_orders, "%"),
    Revenue = dollar(total_revenue), `% Rev` = paste0(pct_revenue, "%"),
    `Avg Order` = dollar(avg_order_size), `Median` = dollar(median_order_size),
    Customers = comma(unique_customers)
  )

kable(yearly_tbl, align = "llrrrrrrrr")
```

# Classification Confidence

```{r plot-confidence, fig.height=5, fig.width=8}
certainty_stripe %>%
  ggplot(aes(x = "", y = n, fill = display_class)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = paste0(display_class, "\n", comma(n), " (", pct, "%)")),
            position = position_stack(vjust = 0.5), size = 4, color = "white",
            fontface = "bold") +
  scale_fill_manual(values = colors_detail) +
  coord_flip() +
  labs(x = "", y = "Customers", fill = "",
       title = "Customer Classification Breakdown",
       subtitle = "Paying customers from Stripe, classified via CRM and BigCommerce signals") +
  theme_buyer +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
```

```{r certainty-table}
cert_tbl <- customer_master %>%
  group_by(Classification = display_class) %>%
  summarise(
    Customers = n(),
    Revenue = dollar(sum(total_spend, na.rm = TRUE)),
    Orders = comma(sum(total_orders, na.rm = TRUE)),
    `Avg LTV` = dollar(mean(total_spend, na.rm = TRUE)),
    .groups = "drop"
  ) %>%
  mutate(`% of Customers` = paste0(round(Customers / sum(Customers) * 100, 1), "%"))

kable(cert_tbl, align = "lrrrrr")
```

# Data Source Coverage

```{r coverage-table}
zoho_emails <- zoho_lookup %>% pull(zoho_email)
bc_emails <- bc_clean %>% filter(!is.na(match_email)) %>% distinct(match_email) %>% pull()
stripe_paying <- customer_master %>% pull(stripe_email)

coverage_tbl <- tibble(
  Metric = c(
    "Stripe paying customers (authority)",
    "Zoho CRM contacts",
    "BigCommerce orders (2023-2025)",
    "Stripe customers matched to Zoho",
    "Stripe customers matched to BigCommerce",
    "Stripe customers with ANY classification signal",
    "Stripe customers with no signal (assumed Residential)"
  ),
  Value = c(
    comma(length(stripe_paying)),
    comma(length(zoho_emails)),
    comma(nrow(bc_clean)),
    paste0(comma(sum(stripe_paying %in% zoho_emails)), " (",
           round(sum(stripe_paying %in% zoho_emails) / length(stripe_paying) * 100, 1), "%)"),
    paste0(comma(sum(stripe_paying %in% bc_emails)), " (",
           round(sum(stripe_paying %in% bc_emails) / length(stripe_paying) * 100, 1), "%)"),
    paste0(comma(sum(customer_master$final_class != "Unknown")), " (",
           round(sum(customer_master$final_class != "Unknown") / nrow(customer_master) * 100, 1), "%)"),
    paste0(comma(sum(customer_master$final_class == "Unknown")), " (",
           no_signal_pct, "%)")
  )
)

kable(coverage_tbl, align = "lr")
```

# Order Economics Deep Dive

```{r order-economics-data}
# BigCommerce has order-level detail with dates — use for deep order analysis
# Enrich with classification from customer_master

order_detail <- bc_clean %>%
  mutate(
    order_month = floor_date(order_date, "month"),
    order_quarter = floor_date(order_date, "quarter"),
    bc_match_name = tolower(trimws(customer_name))
  ) %>%
  left_join(customer_master %>% select(stripe_email, broad_class, final_class),
            by = c("match_email" = "stripe_email")) %>%
  mutate(broad_class = ifelse(is.na(broad_class), "Residential", broad_class))

# Order size buckets
order_detail <- order_detail %>%
  mutate(
    size_bucket = case_when(
      order_total < 50    ~ "Under $50",
      order_total < 150   ~ "$50-$149",
      order_total < 300   ~ "$150-$299",
      order_total < 500   ~ "$300-$499",
      order_total < 1000  ~ "$500-$999",
      order_total < 2500  ~ "$1,000-$2,499",
      order_total < 5000  ~ "$2,500-$4,999",
      order_total >= 5000 ~ "$5,000+"
    ),
    size_bucket = factor(size_bucket, levels = c(
      "Under $50", "$50-$149", "$150-$299", "$300-$499",
      "$500-$999", "$1,000-$2,499", "$2,500-$4,999", "$5,000+"
    )),
    is_core_order = order_total >= 150  # Exclude sample/small orders
  )

# Summary stats
n_orders_total <- nrow(order_detail)
n_orders_core <- sum(order_detail$is_core_order)
pct_core_orders <- round(n_orders_core / n_orders_total * 100, 1)
rev_core <- sum(order_detail$order_total[order_detail$is_core_order], na.rm = TRUE)
rev_total <- sum(order_detail$order_total, na.rm = TRUE)
pct_core_rev <- round(rev_core / rev_total * 100, 1)
```

Understanding order economics is critical to valuing this business. While the company processes a high volume of smaller orders (samples, replacement parts), the revenue engine is driven by substantial project-based orders from both professional and residential customers.

## Order Size Distribution

```{r order-size-dist, fig.height=6}
bucket_summary <- order_detail %>%
  group_by(size_bucket) %>%
  summarise(
    orders = n(),
    revenue = sum(order_total, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    pct_orders = round(orders / sum(orders) * 100, 1),
    pct_revenue = round(revenue / sum(revenue) * 100, 1),
    cum_rev_pct = cumsum(pct_revenue)
  )

gridExtra::grid.arrange(
  bucket_summary %>%
    ggplot(aes(x = size_bucket, y = orders)) +
    geom_col(fill = "#2C5F8A", width = 0.7) +
    geom_text(aes(label = comma(orders)), vjust = -0.3, size = 3.5) +
    scale_y_continuous(labels = comma, expand = expansion(mult = c(0, 0.15))) +
    labs(title = "Order Count by Size", x = "", y = "Orders") +
    theme_buyer + theme(axis.text.x = element_text(angle = 45, hjust = 1)),

  bucket_summary %>%
    ggplot(aes(x = size_bucket, y = revenue)) +
    geom_col(fill = "#E8894A", width = 0.7) +
    geom_text(aes(label = dollar(revenue, accuracy = 1, scale = 1e-3, suffix = "K")),
              vjust = -0.3, size = 3.5) +
    scale_y_continuous(labels = dollar, expand = expansion(mult = c(0, 0.15))) +
    labs(title = "Revenue by Order Size", x = "", y = "Revenue") +
    theme_buyer + theme(axis.text.x = element_text(angle = 45, hjust = 1)),

  ncol = 2
)
```

```{r order-size-table}
bucket_tbl <- bucket_summary %>%
  transmute(
    `Order Size` = size_bucket,
    Orders = comma(orders),
    `% of Orders` = paste0(pct_orders, "%"),
    Revenue = dollar(revenue),
    `% of Revenue` = paste0(pct_revenue, "%"),
    `Cumulative Rev %` = paste0(cum_rev_pct, "%")
  )
kable(bucket_tbl, align = "lrrrrr")
```

> **Key insight:** Orders under $150 represent a disproportionate share of order *count* but a small fraction of *revenue*. The revenue engine is concentrated in orders $300+, which represent the core remodeling and new construction projects that define this business.

## Core Order Metrics (Excluding Orders Under $150)

Small orders (samples, single replacement doors, hardware) distort averages. The following metrics focus on **core orders ($150+)** to reflect the true economics of the project business.

```{r core-metrics-table}
core_metrics <- order_detail %>%
  group_by(broad_class) %>%
  summarise(
    `All Orders - Count` = n(),
    `All Orders - Mean` = dollar(mean(order_total, na.rm = TRUE)),
    `All Orders - Median` = dollar(median(order_total, na.rm = TRUE)),
    `Core Orders ($150+) - Count` = sum(is_core_order),
    `Core Orders ($150+) - Mean` = dollar(mean(order_total[is_core_order], na.rm = TRUE)),
    `Core Orders ($150+) - Median` = dollar(median(order_total[is_core_order], na.rm = TRUE)),
    `Core as % of Revenue` = paste0(round(sum(order_total[is_core_order], na.rm = TRUE) /
      sum(order_total, na.rm = TRUE) * 100, 1), "%"),
    .groups = "drop"
  )

kable(core_metrics %>% rename(Type = broad_class), align = "lrrrrrrr")
```

```{r core-metrics-overall}
overall_core <- order_detail %>%
  summarise(
    all_mean = mean(order_total, na.rm = TRUE),
    all_median = median(order_total, na.rm = TRUE),
    core_mean = mean(order_total[is_core_order], na.rm = TRUE),
    core_median = median(order_total[is_core_order], na.rm = TRUE),
    core_rev_pct = round(sum(order_total[is_core_order], na.rm = TRUE) /
      sum(order_total, na.rm = TRUE) * 100, 1)
  )
```

> Core orders ($150+) represent **`r overall_core$core_rev_pct`%** of total revenue. The core order mean is **`r dollar(overall_core$core_mean)`** vs. the all-orders mean of **`r dollar(overall_core$all_mean)`** — a `r round((overall_core$core_mean / overall_core$all_mean - 1) * 100)`% difference that illustrates how small orders dilute the true project economics.

## Order Size by Customer Type

```{r order-size-by-type, fig.height=6}
bucket_by_type <- order_detail %>%
  group_by(size_bucket, broad_class) %>%
  summarise(orders = n(), revenue = sum(order_total, na.rm = TRUE), .groups = "drop") %>%
  group_by(broad_class) %>%
  mutate(
    pct_orders = round(orders / sum(orders) * 100, 1),
    pct_revenue = round(revenue / sum(revenue) * 100, 1)
  ) %>%
  ungroup()

bucket_by_type %>%
  ggplot(aes(x = size_bucket, y = revenue, fill = broad_class)) +
  geom_col(position = "dodge", width = 0.7) +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = dollar) +
  labs(title = "Revenue by Order Size and Customer Type",
       x = "", y = "Revenue", fill = "Customer Type") +
  theme_buyer + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r order-size-pct-type, fig.height=5}
bucket_by_type %>%
  ggplot(aes(x = size_bucket, y = pct_revenue, fill = broad_class)) +
  geom_col(position = "dodge", width = 0.7) +
  geom_text(aes(label = paste0(pct_revenue, "%")),
            position = position_dodge(width = 0.7), vjust = -0.3, size = 3) +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = function(x) paste0(x, "%"), expand = expansion(mult = c(0, 0.15))) +
  labs(title = "Revenue Concentration by Order Size",
       subtitle = "% of each customer type's revenue from each order size tier",
       x = "", y = "% of Revenue", fill = "Customer Type") +
  theme_buyer + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Revenue Trends Over Time

```{r monthly-revenue, fig.height=5}
monthly_rev <- order_detail %>%
  group_by(order_month) %>%
  summarise(
    revenue = sum(order_total, na.rm = TRUE),
    orders = n(),
    avg_order = mean(order_total, na.rm = TRUE),
    core_orders = sum(is_core_order),
    core_revenue = sum(order_total[is_core_order], na.rm = TRUE),
    core_avg = mean(order_total[is_core_order], na.rm = TRUE),
    .groups = "drop"
  )

monthly_rev %>%
  ggplot(aes(x = order_month, y = revenue)) +
  geom_col(fill = "#2C5F8A", width = 25) +
  geom_smooth(se = FALSE, color = "#E8894A", linewidth = 1.2, method = "loess", span = 0.3) +
  scale_x_date(date_labels = "%b '%y", date_breaks = "3 months") +
  scale_y_continuous(labels = dollar) +
  labs(title = "Monthly Revenue",
       subtitle = "With trend line (BigCommerce orders)",
       x = "", y = "Revenue") +
  theme_buyer + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r monthly-by-type, fig.height=5}
monthly_by_type <- order_detail %>%
  group_by(order_month, broad_class) %>%
  summarise(revenue = sum(order_total, na.rm = TRUE), .groups = "drop")

monthly_by_type %>%
  ggplot(aes(x = order_month, y = revenue, fill = broad_class)) +
  geom_area(alpha = 0.8) +
  scale_fill_manual(values = colors_class) +
  scale_x_date(date_labels = "%b '%y", date_breaks = "3 months") +
  scale_y_continuous(labels = dollar) +
  labs(title = "Monthly Revenue by Customer Type",
       x = "", y = "Revenue", fill = "Customer Type") +
  theme_buyer + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Seasonality & Cyclicality

```{r seasonality, fig.height=5}
seasonal <- order_detail %>%
  mutate(month_num = month(order_date), month_name = month(order_date, label = TRUE)) %>%
  group_by(order_year, month_num, month_name) %>%
  summarise(revenue = sum(order_total, na.rm = TRUE),
            orders = n(), .groups = "drop")

seasonal_avg <- seasonal %>%
  group_by(month_num, month_name) %>%
  summarise(
    avg_revenue = mean(revenue, na.rm = TRUE),
    min_revenue = min(revenue, na.rm = TRUE),
    max_revenue = max(revenue, na.rm = TRUE),
    .groups = "drop"
  )

ggplot() +
  geom_ribbon(data = seasonal_avg, aes(x = month_num, ymin = min_revenue, ymax = max_revenue),
              fill = "#2C5F8A", alpha = 0.15) +
  geom_line(data = seasonal, aes(x = month_num, y = revenue, color = factor(order_year)),
            linewidth = 1) +
  geom_line(data = seasonal_avg, aes(x = month_num, y = avg_revenue),
            linewidth = 1.5, linetype = "dashed", color = "black") +
  scale_x_continuous(breaks = 1:12, labels = month.abb) +
  scale_y_continuous(labels = dollar) +
  scale_color_brewer(palette = "Set1") +
  labs(title = "Revenue Seasonality",
       subtitle = "Monthly revenue by year with 3-year average (dashed) and range (shaded)",
       x = "", y = "Revenue", color = "Year") +
  theme_buyer
```

```{r seasonality-orders, fig.height=5}
seasonal_orders <- order_detail %>%
  mutate(month_num = month(order_date), month_name = month(order_date, label = TRUE)) %>%
  group_by(month_num, month_name) %>%
  summarise(
    avg_orders = mean(n()),
    avg_core_order = mean(order_total[is_core_order], na.rm = TRUE),
    .groups = "drop"
  )

seasonal %>%
  ggplot(aes(x = month_num, y = orders, color = factor(order_year))) +
  geom_line(linewidth = 1) +
  scale_x_continuous(breaks = 1:12, labels = month.abb) +
  scale_y_continuous(labels = comma) +
  scale_color_brewer(palette = "Set1") +
  labs(title = "Order Volume Seasonality",
       subtitle = "Monthly order count by year",
       x = "", y = "Orders", color = "Year") +
  theme_buyer
```

```{r quarterly-growth, fig.height=5}
quarterly <- order_detail %>%
  group_by(order_quarter) %>%
  summarise(
    revenue = sum(order_total, na.rm = TRUE),
    orders = n(),
    core_revenue = sum(order_total[is_core_order], na.rm = TRUE),
    core_avg = mean(order_total[is_core_order], na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    rev_yoy = (revenue / lag(revenue, 4) - 1) * 100,
    quarter_label = paste0("Q", quarter(order_quarter), " ", year(order_quarter))
  )

quarterly %>%
  filter(!is.na(rev_yoy)) %>%
  ggplot(aes(x = order_quarter, y = rev_yoy)) +
  geom_col(aes(fill = rev_yoy > 0), width = 80, show.legend = FALSE) +
  geom_hline(yintercept = 0, linewidth = 0.5) +
  geom_text(aes(label = paste0(round(rev_yoy, 1), "%")), vjust = ifelse(quarterly$rev_yoy[!is.na(quarterly$rev_yoy)] > 0, -0.5, 1.5), size = 3.5) +
  scale_fill_manual(values = c("TRUE" = "#2C5F8A", "FALSE" = "#C0392B")) +
  scale_x_date(date_labels = "%b '%y", date_breaks = "3 months") +
  scale_y_continuous(labels = function(x) paste0(x, "%")) +
  labs(title = "Year-over-Year Quarterly Revenue Growth",
       x = "", y = "YoY Growth %") +
  theme_buyer + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Average Order Value Trends

```{r aov-trends, fig.height=5}
monthly_aov <- order_detail %>%
  group_by(order_month) %>%
  summarise(
    all_mean = mean(order_total, na.rm = TRUE),
    all_median = median(order_total, na.rm = TRUE),
    core_mean = mean(order_total[is_core_order], na.rm = TRUE),
    core_median = median(order_total[is_core_order], na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_longer(-order_month, names_to = "metric", values_to = "value") %>%
  mutate(
    metric = recode(metric,
      "all_mean" = "All Orders - Mean",
      "all_median" = "All Orders - Median",
      "core_mean" = "Core ($150+) - Mean",
      "core_median" = "Core ($150+) - Median"
    ),
    is_core = grepl("Core", metric)
  )

monthly_aov %>%
  ggplot(aes(x = order_month, y = value, color = metric)) +
  geom_line(aes(linewidth = is_core, linetype = grepl("Median", metric)), show.legend = TRUE) +
  scale_linewidth_manual(values = c("TRUE" = 1.2, "FALSE" = 0.6), guide = "none") +
  scale_linetype_manual(values = c("TRUE" = "dashed", "FALSE" = "solid"), guide = "none") +
  scale_color_manual(values = c(
    "All Orders - Mean" = "#B0BEC5", "All Orders - Median" = "#CFD8DC",
    "Core ($150+) - Mean" = "#2C5F8A", "Core ($150+) - Median" = "#E8894A"
  )) +
  scale_x_date(date_labels = "%b '%y", date_breaks = "3 months") +
  scale_y_continuous(labels = dollar) +
  labs(title = "Average Order Value Over Time",
       subtitle = "All orders vs. core orders ($150+); solid = mean, dashed = median",
       x = "", y = "Order Value", color = "") +
  theme_buyer + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Revenue Concentration

```{r revenue-concentration, fig.height=5}
# Customer-level revenue concentration (from Stripe master)
cust_ranked <- customer_master %>%
  arrange(desc(total_spend)) %>%
  mutate(
    cust_rank = row_number(),
    cum_revenue = cumsum(total_spend),
    cum_pct = cum_revenue / sum(total_spend) * 100,
    cust_pct = cust_rank / n() * 100
  )

# Key concentration metrics
top_10_pct <- cust_ranked %>% filter(cust_pct <= 10) %>% slice_tail(n = 1) %>% pull(cum_pct)
top_20_pct <- cust_ranked %>% filter(cust_pct <= 20) %>% slice_tail(n = 1) %>% pull(cum_pct)
top_50_pct <- cust_ranked %>% filter(cust_pct <= 50) %>% slice_tail(n = 1) %>% pull(cum_pct)

cust_ranked %>%
  ggplot(aes(x = cust_pct, y = cum_pct)) +
  geom_line(color = "#2C5F8A", linewidth = 1.2) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "gray60") +
  geom_segment(aes(x = 20, xend = 20, y = 0, yend = top_20_pct),
               linetype = "dotted", color = "#E8894A") +
  geom_segment(aes(x = 0, xend = 20, y = top_20_pct, yend = top_20_pct),
               linetype = "dotted", color = "#E8894A") +
  annotate("text", x = 22, y = top_20_pct - 3,
           label = paste0("Top 20% = ", round(top_20_pct, 1), "% of revenue"),
           hjust = 0, size = 4, fontface = "bold", color = "#E8894A") +
  scale_x_continuous(labels = function(x) paste0(x, "%"), breaks = seq(0, 100, 10)) +
  scale_y_continuous(labels = function(x) paste0(x, "%"), breaks = seq(0, 100, 10)) +
  labs(title = "Revenue Concentration (Lorenz Curve)",
       subtitle = "How revenue is distributed across the customer base",
       x = "% of Customers (ranked by revenue)", y = "Cumulative % of Revenue") +
  theme_buyer
```

```{r concentration-table}
conc_tbl <- tibble(
  Segment = c("Top 1%", "Top 5%", "Top 10%", "Top 20%", "Top 50%", "Bottom 50%"),
  `% of Revenue` = c(
    paste0(round(cust_ranked %>% filter(cust_pct <= 1) %>% slice_tail(n = 1) %>% pull(cum_pct), 1), "%"),
    paste0(round(cust_ranked %>% filter(cust_pct <= 5) %>% slice_tail(n = 1) %>% pull(cum_pct), 1), "%"),
    paste0(round(top_10_pct, 1), "%"),
    paste0(round(top_20_pct, 1), "%"),
    paste0(round(top_50_pct, 1), "%"),
    paste0(round(100 - top_50_pct, 1), "%")
  ),
  Customers = c(
    comma(round(nrow(cust_ranked) * 0.01)),
    comma(round(nrow(cust_ranked) * 0.05)),
    comma(round(nrow(cust_ranked) * 0.10)),
    comma(round(nrow(cust_ranked) * 0.20)),
    comma(round(nrow(cust_ranked) * 0.50)),
    comma(round(nrow(cust_ranked) * 0.50))
  )
)
kable(conc_tbl, align = "lrr")
```

## Revenue Concentration by Customer Type

```{r concentration-by-type, fig.height=5}
conc_by_type <- customer_master %>%
  group_by(broad_class) %>%
  arrange(desc(total_spend)) %>%
  mutate(
    cust_rank = row_number(),
    cum_revenue = cumsum(total_spend),
    cum_pct = cum_revenue / sum(total_spend) * 100,
    cust_pct = cust_rank / n() * 100
  ) %>%
  ungroup()

conc_by_type %>%
  ggplot(aes(x = cust_pct, y = cum_pct, color = broad_class)) +
  geom_line(linewidth = 1.2) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "gray60") +
  scale_color_manual(values = colors_class) +
  scale_x_continuous(labels = function(x) paste0(x, "%")) +
  scale_y_continuous(labels = function(x) paste0(x, "%")) +
  labs(title = "Revenue Concentration by Customer Type",
       subtitle = "Steeper curve = more concentrated in top customers",
       x = "% of Customers (ranked by revenue)",
       y = "Cumulative % of Revenue", color = "Customer Type") +
  theme_buyer
```

## Strategic Opportunity: Professional Segment

```{r strategic-summary}
pro_stats <- customer_master %>% filter(broad_class == "Professional") %>%
  summarise(customers = n(), revenue = sum(total_spend), orders = sum(total_orders),
            avg_ltv = mean(total_spend), median_ltv = median(total_spend),
            avg_orders = mean(total_orders), repeat_rate = mean(is_repeat) * 100,
            avg_order = sum(total_spend) / sum(total_orders))

res_stats <- customer_master %>% filter(broad_class == "Residential") %>%
  summarise(customers = n(), revenue = sum(total_spend), orders = sum(total_orders),
            avg_ltv = mean(total_spend), median_ltv = median(total_spend),
            avg_orders = mean(total_orders), repeat_rate = mean(is_repeat) * 100,
            avg_order = sum(total_spend) / sum(total_orders))

ltv_multiple <- round(pro_stats$avg_ltv / res_stats$avg_ltv, 1)
aov_multiple <- round(pro_stats$avg_order / res_stats$avg_order, 1)
repeat_delta <- round(pro_stats$repeat_rate - res_stats$repeat_rate, 1)
```

The professional segment represents a compelling acquisition thesis:

| Metric | Professional | Residential | Pro Advantage |
|--------|-------------|-------------|---------------|
| Avg LTV | `r dollar(pro_stats$avg_ltv)` | `r dollar(res_stats$avg_ltv)` | **`r ltv_multiple`x** |
| Avg Order Size | `r dollar(pro_stats$avg_order)` | `r dollar(res_stats$avg_order)` | **`r aov_multiple`x** |
| Repeat Rate | `r paste0(round(pro_stats$repeat_rate, 1), "%")` | `r paste0(round(res_stats$repeat_rate, 1), "%")` | **+`r repeat_delta`pp** |
| Avg Orders/Customer | `r round(pro_stats$avg_orders, 1)` | `r round(res_stats$avg_orders, 1)` | **`r round(pro_stats$avg_orders / res_stats$avg_orders, 1)`x** |

> **For Eagle Woodworking:** The professional customer segment delivers `r ltv_multiple`x the lifetime value of residential customers with `r repeat_delta` percentage points higher repeat rates. An acquirer with existing professional relationships and capacity in cabinet door manufacturing can accelerate growth in this high-LTV segment through cross-selling and trade program expansion, while the residential base provides stable, diversified volume.

# Customer Retention & Cohort Analysis

```{r cohort-data}
# Build customer cohorts based on first order date (from BC data)
customer_cohorts <- order_detail %>%
  filter(!is.na(match_email)) %>%
  group_by(match_email) %>%
  mutate(
    first_order_date = min(order_date, na.rm = TRUE),
    first_order_quarter = floor_date(first_order_date, "quarter"),
    first_order_year = year(first_order_date),
    order_num = row_number()
  ) %>%
  ungroup()

# Cohort quarterly retention
cohort_retention <- customer_cohorts %>%
  mutate(
    cohort = format(first_order_quarter, "%Y Q%q"),
    cohort = paste0(year(first_order_quarter), " Q", quarter(first_order_quarter)),
    periods_since = as.numeric(difftime(order_quarter, first_order_quarter, units = "days")) %/% 91
  ) %>%
  group_by(cohort, first_order_quarter, periods_since) %>%
  summarise(customers = n_distinct(match_email), .groups = "drop")

# Get cohort sizes (period 0)
cohort_sizes <- cohort_retention %>%
  filter(periods_since == 0) %>%
  select(cohort, first_order_quarter, cohort_size = customers)

cohort_retention <- cohort_retention %>%
  left_join(cohort_sizes, by = c("cohort", "first_order_quarter")) %>%
  mutate(retention_pct = round(customers / cohort_size * 100, 1))
```

## Cohort Retention Heatmap

```{r cohort-heatmap, fig.height=7, fig.width=10}
cohort_retention %>%
  filter(periods_since <= 8) %>%
  ggplot(aes(x = factor(periods_since), y = reorder(cohort, first_order_quarter), fill = retention_pct)) +
  geom_tile(color = "white", linewidth = 0.5) +
  geom_text(aes(label = paste0(retention_pct, "%")), size = 3, color = "white", fontface = "bold") +
  scale_fill_gradient(low = "#E8894A", high = "#2C5F8A", limits = c(0, 100)) +
  labs(title = "Customer Retention by Quarterly Cohort",
       subtitle = "% of cohort's customers who placed an order in each subsequent quarter",
       x = "Quarters Since First Order", y = "Cohort", fill = "Retention %") +
  theme_buyer +
  theme(panel.grid = element_blank())
```

## New vs. Returning Customers

```{r new-vs-returning, fig.height=5}
new_vs_return <- customer_cohorts %>%
  mutate(
    is_new = order_num == 1,
    customer_status = ifelse(is_new, "New Customer", "Returning Customer")
  ) %>%
  group_by(order_quarter, customer_status) %>%
  summarise(
    customers = n_distinct(match_email),
    revenue = sum(order_total, na.rm = TRUE),
    .groups = "drop"
  )

gridExtra::grid.arrange(
  new_vs_return %>%
    ggplot(aes(x = order_quarter, y = customers, fill = customer_status)) +
    geom_col(width = 80) +
    scale_fill_manual(values = c("New Customer" = "#2C5F8A", "Returning Customer" = "#E8894A")) +
    scale_x_date(date_labels = "%b '%y", date_breaks = "3 months") +
    scale_y_continuous(labels = comma) +
    labs(title = "Customer Acquisition: New vs. Returning",
         x = "", y = "Customers", fill = "") +
    theme_buyer + theme(axis.text.x = element_text(angle = 45, hjust = 1)),

  new_vs_return %>%
    ggplot(aes(x = order_quarter, y = revenue, fill = customer_status)) +
    geom_col(width = 80) +
    scale_fill_manual(values = c("New Customer" = "#2C5F8A", "Returning Customer" = "#E8894A")) +
    scale_x_date(date_labels = "%b '%y", date_breaks = "3 months") +
    scale_y_continuous(labels = dollar) +
    labs(title = "Revenue: New vs. Returning Customers",
         x = "", y = "Revenue", fill = "") +
    theme_buyer + theme(axis.text.x = element_text(angle = 45, hjust = 1)),

  ncol = 2
)
```

```{r new-vs-return-pct, fig.height=5}
new_return_pct <- new_vs_return %>%
  group_by(order_quarter) %>%
  mutate(pct_rev = round(revenue / sum(revenue) * 100, 1)) %>%
  ungroup()

new_return_pct %>%
  ggplot(aes(x = order_quarter, y = pct_rev, fill = customer_status)) +
  geom_area(alpha = 0.85) +
  scale_fill_manual(values = c("New Customer" = "#2C5F8A", "Returning Customer" = "#E8894A")) +
  scale_x_date(date_labels = "%b '%y", date_breaks = "3 months") +
  scale_y_continuous(labels = function(x) paste0(x, "%")) +
  labs(title = "Revenue Mix: New vs. Returning Customers",
       subtitle = "Growing returning-customer share = compounding customer base",
       x = "", y = "% of Revenue", fill = "") +
  theme_buyer + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Time Between Orders

```{r time-between-orders, fig.height=5}
repeat_gaps <- customer_cohorts %>%
  filter(!is.na(match_email)) %>%
  arrange(match_email, order_date) %>%
  group_by(match_email) %>%
  mutate(
    prev_order_date = lag(order_date),
    days_between = as.numeric(difftime(order_date, prev_order_date, units = "days"))
  ) %>%
  filter(!is.na(days_between)) %>%
  ungroup() %>%
  left_join(customer_master %>% select(stripe_email, broad_class),
            by = c("match_email" = "stripe_email")) %>%
  mutate(broad_class = ifelse(is.na(broad_class), "Residential", broad_class))

gap_summary <- repeat_gaps %>%
  group_by(broad_class) %>%
  summarise(
    reorders = n(),
    mean_days = round(mean(days_between)),
    median_days = round(median(days_between)),
    p25_days = round(quantile(days_between, 0.25)),
    p75_days = round(quantile(days_between, 0.75)),
    .groups = "drop"
  )

repeat_gaps %>%
  filter(days_between <= 365) %>%
  ggplot(aes(x = days_between, fill = broad_class)) +
  geom_histogram(binwidth = 14, alpha = 0.7, position = "identity") +
  geom_vline(data = gap_summary, aes(xintercept = median_days, color = broad_class),
             linetype = "dashed", linewidth = 1) +
  scale_fill_manual(values = colors_class) +
  scale_color_manual(values = colors_class) +
  scale_x_continuous(breaks = seq(0, 365, 30)) +
  labs(title = "Time Between Repeat Orders",
       subtitle = "Distribution of days between consecutive orders (capped at 365 days)",
       x = "Days Between Orders", y = "Count", fill = "Customer Type", color = "Median") +
  theme_buyer
```

```{r gap-table}
gap_tbl <- gap_summary %>%
  transmute(
    Type = broad_class,
    `Repeat Orders` = comma(reorders),
    `Mean Gap (days)` = mean_days,
    `Median Gap (days)` = median_days,
    `25th Pctile` = p25_days,
    `75th Pctile` = p75_days
  )
kable(gap_tbl, align = "lrrrrr")
```

> Professional customers reorder on a project-driven cycle. The tight interquartile range suggests predictable demand patterns that support production planning and inventory management.

## Single-Order Customer Risk

```{r single-order-risk, fig.height=5}
single_vs_multi <- customer_master %>%
  mutate(order_group = case_when(
    total_orders == 1 ~ "Single Order",
    total_orders <= 3 ~ "2-3 Orders",
    total_orders <= 5 ~ "4-5 Orders",
    TRUE ~ "6+ Orders"
  )) %>%
  mutate(order_group = factor(order_group, levels = c("Single Order", "2-3 Orders", "4-5 Orders", "6+ Orders"))) %>%
  group_by(order_group, broad_class) %>%
  summarise(
    customers = n(),
    revenue = sum(total_spend, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  group_by(broad_class) %>%
  mutate(
    pct_customers = round(customers / sum(customers) * 100, 1),
    pct_revenue = round(revenue / sum(revenue) * 100, 1)
  ) %>%
  ungroup()

gridExtra::grid.arrange(
  single_vs_multi %>%
    ggplot(aes(x = order_group, y = pct_customers, fill = broad_class)) +
    geom_col(position = "dodge", width = 0.7) +
    geom_text(aes(label = paste0(pct_customers, "%")),
              position = position_dodge(width = 0.7), vjust = -0.3, size = 3.5) +
    scale_fill_manual(values = colors_class) +
    scale_y_continuous(labels = function(x) paste0(x, "%"), expand = expansion(mult = c(0, 0.15))) +
    labs(title = "Customer Distribution by Order Frequency",
         x = "", y = "% of Customers", fill = "Customer Type") +
    theme_buyer,

  single_vs_multi %>%
    ggplot(aes(x = order_group, y = pct_revenue, fill = broad_class)) +
    geom_col(position = "dodge", width = 0.7) +
    geom_text(aes(label = paste0(pct_revenue, "%")),
              position = position_dodge(width = 0.7), vjust = -0.3, size = 3.5) +
    scale_fill_manual(values = colors_class) +
    scale_y_continuous(labels = function(x) paste0(x, "%"), expand = expansion(mult = c(0, 0.15))) +
    labs(title = "Revenue Distribution by Order Frequency",
         x = "", y = "% of Revenue", fill = "Customer Type") +
    theme_buyer,

  ncol = 2
)
```

# Product & Order Composition

```{r product-mix-data}
# Reshape BC order data from wide to long for product analysis
# Products are in columns: Product Name - 1, Product Name - 2, etc.
product_cols <- names(bc_clean)[grepl("^Product Name - \\d+$", names(bc_clean))]
qty_cols <- names(bc_clean)[grepl("^Product Qty - \\d+$", names(bc_clean))]
price_cols <- names(bc_clean)[grepl("^Product Total Price - \\d+$", names(bc_clean))]

# Count products per order
order_detail <- order_detail %>%
  mutate(
    n_line_items = rowSums(!is.na(select(bc_clean[match(order_detail$`Order ID`, bc_clean$`Order ID`), ], all_of(product_cols))) &
                           select(bc_clean[match(order_detail$`Order ID`, bc_clean$`Order ID`), ], all_of(product_cols)) != "", na.rm = TRUE)
  )
```

```{r product-mix-fallback}
# Simpler approach: count non-empty product name columns per order
line_item_counts <- bc_clean %>%
  select(`Order ID`, all_of(product_cols)) %>%
  mutate(across(all_of(product_cols), ~!is.na(.) & . != "")) %>%
  mutate(n_items = rowSums(across(all_of(product_cols)))) %>%
  select(`Order ID`, n_items)

order_detail <- order_detail %>%
  select(-any_of("n_line_items")) %>%
  left_join(line_item_counts, by = "Order ID")
```

## Multi-Item Orders

```{r multi-item, fig.height=5}
item_summary <- order_detail %>%
  mutate(item_group = case_when(
    n_items == 1 ~ "1 Item",
    n_items == 2 ~ "2 Items",
    n_items <= 5 ~ "3-5 Items",
    n_items <= 10 ~ "6-10 Items",
    TRUE ~ "11+ Items"
  )) %>%
  mutate(item_group = factor(item_group, levels = c("1 Item", "2 Items", "3-5 Items", "6-10 Items", "11+ Items"))) %>%
  group_by(item_group) %>%
  summarise(
    orders = n(),
    revenue = sum(order_total, na.rm = TRUE),
    avg_order = mean(order_total, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    pct_orders = round(orders / sum(orders) * 100, 1),
    pct_revenue = round(revenue / sum(revenue) * 100, 1)
  )

item_summary %>%
  select(item_group, pct_orders, pct_revenue) %>%
  pivot_longer(-item_group, names_to = "metric", values_to = "pct") %>%
  mutate(metric = recode(metric, "pct_orders" = "% of Orders", "pct_revenue" = "% of Revenue")) %>%
  ggplot(aes(x = item_group, y = pct, fill = metric)) +
  geom_col(position = "dodge", width = 0.7) +
  geom_text(aes(label = paste0(pct, "%")),
            position = position_dodge(width = 0.7), vjust = -0.3, size = 3.5) +
  scale_fill_manual(values = c("% of Orders" = "#2C5F8A", "% of Revenue" = "#E8894A")) +
  scale_y_continuous(labels = function(x) paste0(x, "%"), expand = expansion(mult = c(0, 0.15))) +
  labs(title = "Order Complexity: Items per Order",
       subtitle = "Multi-item orders correlate with larger project spending",
       x = "", y = "", fill = "") +
  theme_buyer
```

```{r multi-item-table}
item_tbl <- item_summary %>%
  transmute(
    `Items per Order` = item_group,
    Orders = comma(orders),
    `% of Orders` = paste0(pct_orders, "%"),
    Revenue = dollar(revenue),
    `% of Revenue` = paste0(pct_revenue, "%"),
    `Avg Order Size` = dollar(avg_order)
  )
kable(item_tbl, align = "lrrrrr")
```

# Geographic Analysis

```{r geo-data}
# Use shipping state from BC orders
geo_summary <- order_detail %>%
  mutate(state = toupper(trimws(`Shipping State Abbreviation`))) %>%
  filter(!is.na(state) & state != "" & nchar(state) == 2) %>%
  group_by(state) %>%
  summarise(
    orders = n(),
    revenue = sum(order_total, na.rm = TRUE),
    customers = n_distinct(match_email, na.rm = TRUE),
    avg_order = mean(order_total, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(desc(revenue)) %>%
  mutate(
    pct_revenue = round(revenue / sum(revenue) * 100, 1),
    cum_rev_pct = cumsum(pct_revenue),
    rank = row_number()
  )

n_states <- nrow(geo_summary)
top5_rev_pct <- sum(geo_summary$pct_revenue[1:min(5, n_states)])
top10_rev_pct <- sum(geo_summary$pct_revenue[1:min(10, n_states)])
```

## Top Markets by Revenue

```{r geo-top-markets, fig.height=6}
geo_summary %>%
  head(20) %>%
  ggplot(aes(x = reorder(state, revenue), y = revenue)) +
  geom_col(fill = "#2C5F8A", width = 0.7) +
  geom_text(aes(label = paste0(dollar(revenue, accuracy = 1, scale = 1e-3, suffix = "K"),
                                " (", pct_revenue, "%)")),
            hjust = -0.05, size = 3.5) +
  scale_y_continuous(labels = dollar, expand = expansion(mult = c(0, 0.3))) +
  coord_flip() +
  labs(title = "Top 20 Markets by Revenue",
       subtitle = paste0("Top 5 states = ", round(top5_rev_pct, 1), "% of revenue | ",
                         "Top 10 = ", round(top10_rev_pct, 1), "%"),
       x = "", y = "Revenue") +
  theme_buyer
```

## Geographic Mix by Customer Type

```{r geo-by-type, fig.height=6}
geo_by_type <- order_detail %>%
  mutate(state = toupper(trimws(`Shipping State Abbreviation`))) %>%
  filter(!is.na(state) & state != "" & nchar(state) == 2) %>%
  group_by(state, broad_class) %>%
  summarise(revenue = sum(order_total, na.rm = TRUE), .groups = "drop") %>%
  group_by(state) %>%
  mutate(total_rev = sum(revenue)) %>%
  ungroup() %>%
  filter(state %in% geo_summary$state[1:15])

geo_by_type %>%
  ggplot(aes(x = reorder(state, total_rev), y = revenue, fill = broad_class)) +
  geom_col(width = 0.7) +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = dollar) +
  coord_flip() +
  labs(title = "Top 15 Markets: Professional vs. Residential Mix",
       x = "", y = "Revenue", fill = "Customer Type") +
  theme_buyer
```

## Geographic Concentration

```{r geo-concentration, fig.height=5}
geo_summary %>%
  ggplot(aes(x = rank, y = cum_rev_pct)) +
  geom_line(color = "#2C5F8A", linewidth = 1.2) +
  geom_point(data = geo_summary %>% filter(rank <= 10), color = "#E8894A", size = 2.5) +
  geom_text(data = geo_summary %>% filter(rank <= 10),
            aes(label = state), vjust = -1, size = 3.5, fontface = "bold") +
  geom_hline(yintercept = 80, linetype = "dashed", color = "gray50") +
  annotate("text", x = n_states * 0.7, y = 82, label = "80% of revenue", color = "gray40", size = 4) +
  scale_x_continuous(breaks = seq(0, n_states, 5)) +
  scale_y_continuous(labels = function(x) paste0(x, "%"), limits = c(0, 105)) +
  labs(title = "Geographic Revenue Concentration",
       subtitle = paste0("Revenue comes from ", n_states, " states — ",
                         "top 10 account for ", round(top10_rev_pct, 1), "%"),
       x = "Number of States (ranked by revenue)", y = "Cumulative % of Revenue") +
  theme_buyer
```

```{r geo-table}
geo_tbl <- geo_summary %>%
  head(15) %>%
  transmute(
    Rank = rank, State = state,
    Orders = comma(orders), Customers = comma(customers),
    Revenue = dollar(revenue), `% of Rev` = paste0(pct_revenue, "%"),
    `Cum Rev %` = paste0(cum_rev_pct, "%"),
    `Avg Order` = dollar(avg_order)
  )
kable(geo_tbl, align = "rlrrrrrr")
```

> The business has **nationwide reach** across `r n_states` states with manageable concentration — no single state dominates dangerously. This geographic diversification reduces risk and provides multiple growth vectors.

# Revenue Quality

```{r revenue-quality}
# Net revenue from Stripe (refunds)
total_gross <- sum(customer_master$total_spend, na.rm = TRUE)
total_refunds <- sum(customer_master$total_refunded, na.rm = TRUE)
total_net <- total_gross - total_refunds
refund_rate <- round(total_refunds / total_gross * 100, 2)

# By customer type
rev_quality <- customer_master %>%
  group_by(broad_class) %>%
  summarise(
    gross_revenue = sum(total_spend, na.rm = TRUE),
    refunds = sum(total_refunded, na.rm = TRUE),
    net_revenue = gross_revenue - refunds,
    refund_rate = round(refunds / gross_revenue * 100, 2),
    .groups = "drop"
  )
```

## Refund & Net Revenue Analysis

```{r rev-quality-table}
rq_tbl <- rev_quality %>%
  transmute(
    Type = broad_class,
    `Gross Revenue` = dollar(gross_revenue),
    Refunds = dollar(refunds),
    `Net Revenue` = dollar(net_revenue),
    `Refund Rate` = paste0(refund_rate, "%")
  )

overall_rq <- tibble(
  Type = "**Overall**",
  `Gross Revenue` = dollar(total_gross),
  Refunds = dollar(total_refunds),
  `Net Revenue` = dollar(total_net),
  `Refund Rate` = paste0(refund_rate, "%")
)

kable(bind_rows(rq_tbl, overall_rq), align = "lrrrr")
```

> A `r refund_rate`% refund rate indicates strong product quality, accurate order fulfillment, and effective customer support. This is well within industry norms for custom and semi-custom building products.

## Monthly Revenue Trajectory

```{r revenue-trajectory, fig.height=5}
monthly_rev_enhanced <- customer_cohorts %>%
  group_by(order_month) %>%
  summarise(
    gross_revenue = sum(order_total, na.rm = TRUE),
    orders = n(),
    new_customers = n_distinct(match_email[order_num == 1], na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    trailing_3mo = zoo::rollmean(gross_revenue, k = 3, fill = NA, align = "right"),
    trailing_6mo = zoo::rollmean(gross_revenue, k = 6, fill = NA, align = "right")
  )

monthly_rev_enhanced %>%
  ggplot(aes(x = order_month)) +
  geom_col(aes(y = gross_revenue), fill = "#2C5F8A", alpha = 0.3, width = 25) +
  geom_line(aes(y = trailing_3mo, color = "3-Month Avg"), linewidth = 1) +
  geom_line(aes(y = trailing_6mo, color = "6-Month Avg"), linewidth = 1.2) +
  scale_color_manual(values = c("3-Month Avg" = "#E8894A", "6-Month Avg" = "#2C5F8A")) +
  scale_x_date(date_labels = "%b '%y", date_breaks = "3 months") +
  scale_y_continuous(labels = dollar) +
  labs(title = "Revenue Trajectory with Moving Averages",
       subtitle = "Smoothed trend lines filter seasonal noise",
       x = "", y = "Revenue", color = "") +
  theme_buyer + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# Professional Segment Deep Dive

```{r pro-subsegments, fig.height=6}
# Professional sub-segments from Zoho business type
pro_subseg <- customer_master %>%
  filter(broad_class == "Professional") %>%
  left_join(zoho_classified %>%
    filter(!is.na(zoho_email) & zoho_email != "") %>%
    group_by(zoho_email) %>% slice(1) %>% ungroup() %>%
    select(zoho_email, zoho_business_type),
    by = c("stripe_email" = "zoho_email")) %>%
  mutate(
    subsegment = case_when(
      !is.na(zoho_business_type) & zoho_business_type != "" ~ str_to_title(zoho_business_type),
      TRUE ~ "Other / Unspecified"
    )
  )

pro_subseg_summary <- pro_subseg %>%
  group_by(subsegment) %>%
  summarise(
    customers = n(),
    revenue = sum(total_spend, na.rm = TRUE),
    avg_ltv = mean(total_spend, na.rm = TRUE),
    repeat_rate = round(mean(is_repeat) * 100, 1),
    .groups = "drop"
  ) %>%
  arrange(desc(revenue)) %>%
  head(10)

pro_subseg_summary %>%
  ggplot(aes(x = reorder(subsegment, revenue), y = revenue)) +
  geom_col(fill = "#2C5F8A", width = 0.7) +
  geom_text(aes(label = paste0(dollar(revenue, accuracy = 1, scale = 1e-3, suffix = "K"),
                                " | ", customers, " customers")),
            hjust = -0.05, size = 3.5) +
  scale_y_continuous(labels = dollar, expand = expansion(mult = c(0, 0.35))) +
  coord_flip() +
  labs(title = "Professional Sub-Segments by Revenue",
       subtitle = "Top 10 professional categories",
       x = "", y = "Revenue") +
  theme_buyer
```

```{r pro-subseg-table}
pro_sub_tbl <- pro_subseg_summary %>%
  transmute(
    Segment = subsegment,
    Customers = comma(customers),
    Revenue = dollar(revenue),
    `Avg LTV` = dollar(avg_ltv),
    `Repeat Rate` = paste0(repeat_rate, "%")
  )
kable(pro_sub_tbl, align = "lrrrr")
```

## Top Professional Accounts

```{r top-accounts, fig.height=6}
top_pros <- customer_master %>%
  filter(broad_class == "Professional") %>%
  arrange(desc(total_spend)) %>%
  head(25) %>%
  mutate(
    display_name = paste0("Account #", row_number()),
    label = paste0(dollar(total_spend), " | ", total_orders, " orders")
  )

top_pros %>%
  ggplot(aes(x = reorder(display_name, total_spend), y = total_spend)) +
  geom_col(fill = "#2C5F8A", width = 0.7) +
  geom_text(aes(label = label), hjust = -0.05, size = 3) +
  scale_y_continuous(labels = dollar, expand = expansion(mult = c(0, 0.3))) +
  coord_flip() +
  labs(title = "Top 25 Professional Accounts by Lifetime Value",
       subtitle = "Anonymized — demonstrates depth of professional relationships",
       x = "", y = "Lifetime Revenue") +
  theme_buyer
```

```{r top-accounts-summary}
top25_rev <- sum(top_pros$total_spend)
top25_pct <- round(top25_rev / sum(customer_master$total_spend[customer_master$broad_class == "Professional"]) * 100, 1)
```

> The top 25 professional accounts represent **`r dollar(top25_rev)`** in lifetime revenue (**`r top25_pct`%** of professional revenue). These are deeply embedded relationships with high switching costs — exactly the type of recurring professional demand that Eagle Woodworking can scale with additional capacity.

## Trade Program Conversion

```{r trade-conversion}
# Customers who showed trade interest vs. became active buyers
trade_interested <- zoho_classified %>%
  filter(sig_trade_interest | sig_trade_interest_meta | sig_trade_program) %>%
  filter(!is.na(zoho_email) & zoho_email != "") %>%
  distinct(zoho_email)

trade_purchased <- customer_master %>%
  filter(stripe_email %in% trade_interested$zoho_email)

trade_conv_rate <- round(nrow(trade_purchased) / nrow(trade_interested) * 100, 1)
trade_rev <- sum(trade_purchased$total_spend, na.rm = TRUE)
trade_avg_ltv <- mean(trade_purchased$total_spend, na.rm = TRUE)
```

```{r trade-table}
trade_tbl <- tibble(
  Metric = c("CRM contacts with trade program interest",
             "Converted to paying customer",
             "Conversion rate",
             "Revenue from converted trade contacts",
             "Avg LTV of trade program customers"),
  Value = c(comma(nrow(trade_interested)),
            comma(nrow(trade_purchased)),
            paste0(trade_conv_rate, "%"),
            dollar(trade_rev),
            dollar(trade_avg_ltv))
)
kable(trade_tbl, align = "lr")
```

> The trade program pipeline contains **`r comma(nrow(trade_interested))`** contacts who expressed interest. At a `r trade_conv_rate`% conversion rate, there is significant headroom to convert more professionals through targeted outreach — a low-cost growth lever for an acquirer with existing trade relationships.

# Methodology

## Data Sources

| Source | Role | Records |
|--------|------|---------|
| **Stripe** | Authoritative payment data: customer totals, order counts, revenue | `r comma(nrow(stripe_customers))` raw records |
| **Zoho CRM Contacts** | Customer classification: type, trade program, business info | `r comma(nrow(zoho_contacts))` contacts |
| **Zoho CRM Accounts** | Additional classification source with overlapping fields | `r comma(nrow(zoho_accounts))` accounts |
| **BigCommerce Orders** | Order-level detail with dates for trends and order economics | `r comma(nrow(bc_orders))` orders |
| **BigCommerce Customers** | Customer-level data with Company field | `r comma(nrow(bc_customers))` customers |

## Classification Logic

Customers are classified as **Professional** if they exhibit any **strong signal** or two or more **weak signals**:

**Strong signals** (any one is sufficient):

- CRM `Customer Type` = commercial, professional, contractor, builder, designer, etc.
- CRM `Business Type` is set (e.g., general contractor, cabinet shop, property management)
- CRM `Contact Type` = professional, commercial, contractor, trade
- CRM `Trade Program Status` is active
- CRM `Trade Program Interest` expressed
- CRM `Trade Program` = true (boolean field)
- CRM `professionalType` metadata (remodeler, home builder, handyman, cabinet shop, interior designer, etc.)
- CRM `customerType` metadata = professional or both
- CRM `tradeProgramInterest` metadata = yes
- CRM `proProjectType` metadata is set (indicates professional project context)
- CRM `Projects per Year` is set (indicates professional order volume)
- `Business ID` or `Business Entity` on file
- Tax exempt status

**Weak signals** (require two together):

- Company name on file (after filtering junk entries like personal names, "home", "yes", "kitchen")
- Non-personal email domain (i.e., not Gmail, Yahoo, Outlook, etc.)

**Residential**: Explicitly tagged as homeowner/residential in CRM `Customer Type`, `Business Type`, `Contact Type`, or `customerType` metadata, with no professional signals.

**Unknown (assumed Residential)**: No signals in any direction. Conservatively grouped with Residential but tracked separately for transparency.

## Scope

Only Stripe customers active in the 2023--2025 period are included. A customer is considered active if their Stripe account was created in 2023 or later, OR if they have a BigCommerce order dated within 2023--2025.

## Merge Strategy

All systems are joined on **email address** (lowercased, trimmed). Stripe serves as the master customer list (deduplicated by email, filtered to paying customers with activity in 2023--2025). Zoho CRM provides the primary classification via 14 strong signals and 2 weak signals. BigCommerce provides fallback signals (shipping company, customer group) and order-level date data for yearly trend analysis.

---

*Report generated `r format(Sys.time(), '%B %d, %Y at %I:%M %p')`*
