---
title: "Customer Segmentation Analysis"
subtitle: "Residential vs. Professional Order Breakdown, 2023-2025"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
    fig_width: 10
    fig_height: 6
    css: !expr NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE,
  fig.align = "center", out.width = "100%"
)

library(dplyr)
library(ggplot2)
library(readr)
library(stringr)
library(tidyr)
library(lubridate)
library(scales)
library(gridExtra)
library(knitr)
```

```{r load-data}
bc_orders <- read_csv("orders-2026-03-25.csv", show_col_types = FALSE)
zoho_contacts <- read_csv("Contacts_2026_03_25.csv", show_col_types = FALSE)
stripe_customers <- read_csv("stripe_unified_customers.csv", show_col_types = FALSE)
```

```{r prep-bigcommerce}
bc_clean <- bc_orders %>%
  mutate(
    order_date = mdy(`Order Date`),
    order_year = year(order_date),
    order_total = as.numeric(gsub("[^0-9.]", "", `Order Total (inc tax)`)),
    customer_email = tolower(trimws(`Customer Email`)),
    billing_email = tolower(trimws(`Billing Email`)),
    shipping_company = tolower(trimws(`Shipping Company`)),
    billing_company = tolower(trimws(`Billing Company`)),
    customer_group = tolower(trimws(`Customer Group Name`)),
    customer_name = trimws(`Customer Name`),
    billing_name = trimws(`Billing Name`),
    shipping_name = trimws(`Shipping Name`)
  ) %>%
  filter(order_year %in% c(2023, 2024, 2025)) %>%
  mutate(
    match_email = case_when(
      !is.na(customer_email) & customer_email != "" ~ customer_email,
      !is.na(billing_email) & billing_email != ""   ~ billing_email,
      TRUE ~ NA_character_
    )
  )
```

```{r prep-zoho}
zoho_clean <- zoho_contacts %>%
  mutate(
    zoho_email = tolower(trimws(Email)),
    zoho_customer_type = tolower(trimws(`Customer Type`)),
    zoho_business_type = tolower(trimws(`Business Type`)),
    zoho_contact_type = tolower(trimws(`Contact Type`)),
    zoho_lead_source = tolower(trimws(`Lead Source`)),
    zoho_trade_status = tolower(trimws(`Trade Program Status`)),
    zoho_trade_interest = tolower(trimws(`Trade Program Interest`)),
    zoho_professional_type = tolower(trimws(ifelse(
      "professionalType" %in% names(.), `professionalType`, NA_character_
    ))),
    zoho_business_id = trimws(`Business ID`),
    zoho_business_entity = trimws(`Business Entity`),
    zoho_tax_exempt = tolower(trimws(`Tax Exempt?`)),
    zoho_company = tolower(trimws(`Account Name`)),
    zoho_first_name = trimws(`First Name`),
    zoho_last_name = trimws(`Last Name`),
    zoho_full_name = trimws(paste(zoho_first_name, zoho_last_name))
  )
```

```{r classify-zoho}
personal_email_domains <- c(
  "gmail.com", "yahoo.com", "hotmail.com", "outlook.com", "aol.com",
  "icloud.com", "me.com", "mac.com", "live.com", "msn.com",
  "comcast.net", "att.net", "verizon.net", "sbcglobal.net", "cox.net",
  "charter.net", "earthlink.net", "optonline.net", "frontier.com",
  "windstream.net", "centurylink.net", "embarqmail.com", "suddenlink.net",
  "mail.com", "email.com", "ymail.com", "rocketmail.com", "protonmail.com",
  "zoho.com", "fastmail.com", "hushmail.com", "inbox.com", "gmx.com"
)

company_junk <- c(
  "", "n/a", "na", "none", "no", "self", "retired", "home", "homeowner",
  "yes", "kitchen", "bath", "bathroom", "bathroom remodel", "cabinet doors",
  "stock cabinets", "custom cabinets", "cabinets", "google", "bigcommerce",
  "reflectiz bigcommerce", "facebook", "instagram"
)

zoho_classified <- zoho_clean %>%
  mutate(
    email_domain = str_extract(zoho_email, "(?<=@)[^@]+$"),
    has_business_email = !is.na(email_domain) & !(email_domain %in% personal_email_domains),
    sig_customer_type = zoho_customer_type %in% c(
      "professional", "commercial", "contractor", "builder", "designer",
      "architect", "trade", "dealer", "wholesale", "business"
    ),
    sig_business_type = !is.na(zoho_business_type) & zoho_business_type != "" &
      zoho_business_type != "homeowner" & zoho_business_type != "residential",
    sig_contact_type = zoho_contact_type %in% c(
      "professional", "commercial", "contractor", "trade", "dealer", "business"
    ),
    sig_trade_status = !is.na(zoho_trade_status) & zoho_trade_status != "" &
      zoho_trade_status != "none" & zoho_trade_status != "n/a",
    sig_trade_interest = !is.na(zoho_trade_interest) & zoho_trade_interest != "" &
      zoho_trade_interest != "no" & zoho_trade_interest != "none" &
      zoho_trade_interest != "n/a",
    sig_professional_type = !is.na(zoho_professional_type) &
      zoho_professional_type != "" & zoho_professional_type != "homeowner",
    sig_business_id = !is.na(zoho_business_id) & zoho_business_id != "",
    sig_business_entity = !is.na(zoho_business_entity) & zoho_business_entity != "",
    sig_tax_exempt = !is.na(zoho_tax_exempt) & zoho_tax_exempt %in% c("yes", "true", "y"),
    sig_company_raw = !is.na(zoho_company) &
      !(zoho_company %in% company_junk) &
      !(zoho_company == tolower(paste(zoho_first_name, zoho_last_name))) &
      !(zoho_company == tolower(zoho_last_name)),
    sig_email_raw = has_business_email,
    sig_residential = zoho_customer_type %in% c("homeowner", "residential") |
      zoho_business_type %in% c("homeowner", "residential") |
      zoho_contact_type %in% c("homeowner", "residential"),
    strong_signal_count = sig_customer_type + sig_business_type + sig_contact_type +
      sig_trade_status + sig_trade_interest + sig_professional_type +
      sig_business_id + sig_business_entity + sig_tax_exempt,
    weak_signal_count = sig_company_raw + sig_email_raw,
    pro_signal_count = strong_signal_count + weak_signal_count,
    is_professional = (strong_signal_count >= 1) | (weak_signal_count >= 2),
    customer_class = case_when(
      is_professional & !sig_residential ~ "Professional",
      is_professional & sig_residential  ~ "Professional",
      sig_residential                    ~ "Residential",
      TRUE                               ~ "Unknown"
    ),
    classification_confidence = case_when(
      strong_signal_count >= 2 ~ "High",
      strong_signal_count == 1 ~ "Medium",
      weak_signal_count >= 2   ~ "Low",
      sig_residential          ~ "Medium",
      TRUE                     ~ "No Signal"
    )
  )
```

```{r merge-orders}
zoho_lookup <- zoho_classified %>%
  filter(!is.na(zoho_email) & zoho_email != "") %>%
  group_by(zoho_email) %>%
  slice_max(pro_signal_count, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  select(zoho_email, customer_class, classification_confidence, pro_signal_count,
         zoho_company, zoho_customer_type, zoho_business_type, zoho_trade_status,
         starts_with("sig_"))

orders_merged <- bc_clean %>%
  left_join(zoho_lookup, by = c("match_email" = "zoho_email")) %>%
  mutate(
    bc_has_company = !is.na(shipping_company) & shipping_company != "" &
      !shipping_company %in% c("n/a", "na", "none", "-"),
    bc_group_pro = customer_group %in% c(
      "professional", "commercial", "trade", "wholesale", "dealer",
      "contractor", "builder", "business"
    ),
    final_class = case_when(
      !is.na(customer_class) ~ customer_class,
      bc_has_company | bc_group_pro ~ "Professional",
      TRUE ~ "Unknown"
    ),
    display_class = ifelse(final_class == "Unknown", "Residential (assumed)", final_class),
    broad_class = ifelse(final_class == "Professional", "Professional", "Residential")
  )
```

```{r stripe-integration}
stripe_clean <- stripe_customers %>%
  mutate(
    stripe_email = tolower(trimws(Email)),
    stripe_name = trimws(Name),
    stripe_total_spend = as.numeric(gsub("[^0-9.]", "", `Total Spend`)),
    stripe_payment_count = as.numeric(`Payment Count`),
    stripe_avg_order = as.numeric(gsub("[^0-9.]", "", `Average Order`)),
    stripe_refunded = as.numeric(gsub("[^0-9.]", "", `Refunded Volume`)),
    stripe_created = ymd_hms(`Created (UTC)`, quiet = TRUE),
    stripe_created_year = year(stripe_created)
  ) %>%
  filter(!is.na(stripe_email) & stripe_email != "")

stripe_lookup <- stripe_clean %>%
  group_by(stripe_email) %>%
  summarise(
    stripe_total_spend = sum(stripe_total_spend, na.rm = TRUE),
    stripe_payment_count = sum(stripe_payment_count, na.rm = TRUE),
    stripe_avg_order = mean(stripe_avg_order, na.rm = TRUE),
    stripe_refunded = sum(stripe_refunded, na.rm = TRUE),
    stripe_first_created = min(stripe_created, na.rm = TRUE),
    .groups = "drop"
  )

orders_merged <- orders_merged %>%
  left_join(stripe_lookup, by = c("match_email" = "stripe_email"))

bc_emails <- orders_merged %>%
  filter(!is.na(match_email)) %>% distinct(match_email) %>% pull()
stripe_emails <- stripe_lookup %>% pull(stripe_email)
bc_only <- setdiff(bc_emails, stripe_emails)
stripe_only <- setdiff(stripe_emails, bc_emails)
both <- intersect(bc_emails, stripe_emails)

stripe_only_classified <- stripe_clean %>%
  filter(stripe_email %in% stripe_only) %>%
  left_join(
    zoho_lookup %>% select(zoho_email, customer_class, classification_confidence),
    by = c("stripe_email" = "zoho_email")
  ) %>%
  mutate(
    final_class = ifelse(is.na(customer_class), "Unknown", customer_class),
    broad_class = ifelse(final_class == "Professional", "Professional", "Residential")
  )

revenue_comparison <- orders_merged %>%
  filter(!is.na(match_email) & !is.na(stripe_total_spend)) %>%
  group_by(match_email) %>%
  summarise(bc_revenue = sum(order_total, na.rm = TRUE),
            stripe_revenue = first(stripe_total_spend), .groups = "drop") %>%
  summarise(customers = n(), total_bc_revenue = sum(bc_revenue),
            total_stripe_revenue = sum(stripe_revenue),
            bc_capture_rate = round(total_bc_revenue / total_stripe_revenue * 100, 1))
```

```{r compute-summaries}
# Analysis summary by year
analysis_summary <- orders_merged %>%
  group_by(order_year, broad_class) %>%
  summarise(
    order_count = n(),
    total_revenue = sum(order_total, na.rm = TRUE),
    avg_order_size = mean(order_total, na.rm = TRUE),
    median_order_size = median(order_total, na.rm = TRUE),
    unique_customers = n_distinct(match_email, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  group_by(order_year) %>%
  mutate(
    pct_orders = round(order_count / sum(order_count) * 100, 1),
    pct_revenue = round(total_revenue / sum(total_revenue) * 100, 1)
  ) %>%
  ungroup()

# Repeat rate
repeat_analysis <- orders_merged %>%
  group_by(broad_class, match_email) %>%
  summarise(order_count = n(), total_spent = sum(order_total, na.rm = TRUE),
            first_order = min(order_date, na.rm = TRUE),
            last_order = max(order_date, na.rm = TRUE), .groups = "drop") %>%
  filter(!is.na(match_email)) %>%
  mutate(is_repeat = order_count > 1)

repeat_summary <- repeat_analysis %>%
  group_by(broad_class) %>%
  summarise(total_customers = n(), repeat_customers = sum(is_repeat),
            repeat_rate = round(repeat_customers / total_customers * 100, 1),
            avg_orders_per_customer = round(mean(order_count), 2),
            avg_ltv = round(mean(total_spent), 2), .groups = "drop")

# Repeat by year
repeat_by_year <- orders_merged %>%
  filter(!is.na(match_email)) %>%
  arrange(match_email, order_date) %>%
  group_by(match_email) %>%
  mutate(cumulative_order_num = row_number(), is_repeat_order = cumulative_order_num > 1) %>%
  ungroup() %>%
  group_by(order_year, broad_class) %>%
  summarise(total_orders = n(), repeat_orders = sum(is_repeat_order),
            repeat_order_rate = round(repeat_orders / total_orders * 100, 1),
            .groups = "drop")

# Certainty
certainty_summary <- orders_merged %>%
  group_by(order_year) %>%
  summarise(total = n(), classified_pro = sum(final_class == "Professional"),
            classified_res = sum(final_class == "Residential"),
            no_signal = sum(final_class == "Unknown"),
            pct_no_signal = round(no_signal / total * 100, 1),
            matched_to_zoho = sum(!is.na(customer_class)),
            pct_matched = round(matched_to_zoho / total * 100, 1), .groups = "drop")

# Totals
total_orders <- nrow(orders_merged)
total_revenue <- sum(orders_merged$order_total, na.rm = TRUE)
no_signal_pct <- round(sum(orders_merged$final_class == "Unknown") / total_orders * 100, 1)
```

```{r theme-setup}
theme_buyer <- theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", size = 15),
    plot.subtitle = element_text(color = "gray40", size = 11),
    legend.position = "bottom",
    panel.grid.minor = element_blank()
  )

colors_class <- c("Professional" = "#2C5F8A", "Residential" = "#E8894A")
colors_detail <- c("Professional" = "#2C5F8A", "Residential" = "#E8894A",
                    "Residential (assumed)" = "#F5C285")
```

# Executive Summary

This report analyzes **`r comma(total_orders)`** orders totaling **`r dollar(total_revenue)`** across 2023--2025, classifying each order as either **Professional** (contractors, builders, designers, commercial buyers) or **Residential** (homeowners).

```{r exec-summary-table}
exec_tbl <- orders_merged %>%
  group_by(`Customer Type` = broad_class) %>%
  summarise(
    Orders = n(),
    Revenue = sum(order_total, na.rm = TRUE),
    `Avg Order` = mean(order_total, na.rm = TRUE),
    Customers = n_distinct(match_email, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    `% of Orders` = paste0(round(Orders / sum(Orders) * 100, 1), "%"),
    `% of Revenue` = paste0(round(Revenue / sum(Revenue) * 100, 1), "%"),
    Revenue = dollar(Revenue),
    `Avg Order` = dollar(`Avg Order`)
  ) %>%
  select(`Customer Type`, Orders, `% of Orders`, Revenue, `% of Revenue`, `Avg Order`, Customers)

kable(exec_tbl, format.args = list(big.mark = ","), align = "lrrrrrr")
```

> **Classification certainty:** `r no_signal_pct`% of orders had no signal indicating either customer type and are assumed Residential. These are shown separately in the confidence chart below.

---

# Order Volume by Customer Type

```{r plot-order-count, fig.height=5}
analysis_summary %>%
  ggplot(aes(x = factor(order_year), y = order_count, fill = broad_class)) +
  geom_col(position = "dodge", width = 0.7) +
  geom_text(aes(label = comma(order_count)),
            position = position_dodge(width = 0.7), vjust = -0.5, size = 4) +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = comma, expand = expansion(mult = c(0, 0.15))) +
  labs(x = "Year", y = "Order Count", fill = "Customer Type") +
  theme_buyer
```

# Revenue by Customer Type

```{r plot-revenue, fig.height=5}
analysis_summary %>%
  ggplot(aes(x = factor(order_year), y = total_revenue, fill = broad_class)) +
  geom_col(position = "dodge", width = 0.7) +
  geom_text(aes(label = dollar(total_revenue, accuracy = 1)),
            position = position_dodge(width = 0.7), vjust = -0.5, size = 3.5) +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = dollar, expand = expansion(mult = c(0, 0.15))) +
  labs(x = "Year", y = "Total Revenue", fill = "Customer Type") +
  theme_buyer
```

# Revenue Share

```{r plot-revenue-share, fig.height=5}
analysis_summary %>%
  ggplot(aes(x = factor(order_year), y = pct_revenue, fill = broad_class)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = paste0(pct_revenue, "%")),
            position = position_stack(vjust = 0.5), size = 5, color = "white",
            fontface = "bold") +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = function(x) paste0(x, "%")) +
  labs(x = "Year", y = "% of Revenue", fill = "Customer Type") +
  theme_buyer
```

# Average Order Size

```{r plot-avg-order, fig.height=5}
analysis_summary %>%
  ggplot(aes(x = factor(order_year), y = avg_order_size, fill = broad_class)) +
  geom_col(position = "dodge", width = 0.7) +
  geom_text(aes(label = dollar(avg_order_size, accuracy = 1)),
            position = position_dodge(width = 0.7), vjust = -0.5, size = 4) +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = dollar, expand = expansion(mult = c(0, 0.15))) +
  labs(x = "Year", y = "Avg Order Size", fill = "Customer Type") +
  theme_buyer
```

# Year-over-Year Summary

```{r yearly-table}
yearly_tbl <- analysis_summary %>%
  mutate(
    total_revenue = dollar(total_revenue),
    avg_order_size = dollar(avg_order_size),
    median_order_size = dollar(median_order_size)
  ) %>%
  select(
    Year = order_year, Type = broad_class, Orders = order_count,
    `% Orders` = pct_orders, Revenue = total_revenue, `% Rev` = pct_revenue,
    `Avg Order` = avg_order_size, `Median Order` = median_order_size,
    Customers = unique_customers
  )

kable(yearly_tbl, align = "llrrrrrrr")
```

# Repeat Customers

## Overall Repeat Rate

```{r plot-repeat-rate, fig.height=5, fig.width=8}
repeat_summary %>%
  ggplot(aes(x = broad_class, y = repeat_rate, fill = broad_class)) +
  geom_col(width = 0.5) +
  geom_text(aes(label = paste0(repeat_rate, "%")), vjust = -0.5, size = 5, fontface = "bold") +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = function(x) paste0(x, "%"),
                     expand = expansion(mult = c(0, 0.15))) +
  labs(x = "", y = "Repeat Rate", fill = "Customer Type",
       subtitle = "Customers with 2+ orders (2023-2025)") +
  theme_buyer
```

```{r repeat-table}
repeat_tbl <- repeat_summary %>%
  mutate(avg_ltv = dollar(avg_ltv)) %>%
  select(
    Type = broad_class, Customers = total_customers, `Repeat Customers` = repeat_customers,
    `Repeat Rate` = repeat_rate, `Avg Orders/Customer` = avg_orders_per_customer,
    `Avg LTV` = avg_ltv
  )

kable(repeat_tbl, align = "lrrrrr")
```

## Repeat Rate by Year

```{r plot-repeat-by-year, fig.height=5}
repeat_by_year %>%
  ggplot(aes(x = factor(order_year), y = repeat_order_rate, fill = broad_class)) +
  geom_col(position = "dodge", width = 0.7) +
  geom_text(aes(label = paste0(repeat_order_rate, "%")),
            position = position_dodge(width = 0.7), vjust = -0.5, size = 4) +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = function(x) paste0(x, "%"),
                     expand = expansion(mult = c(0, 0.15))) +
  labs(x = "Year", y = "Repeat Order %", fill = "Customer Type",
       subtitle = "% of orders from returning customers") +
  theme_buyer
```

# Customer Lifetime Value

```{r plot-ltv, fig.height=5, fig.width=8}
repeat_summary %>%
  ggplot(aes(x = broad_class, y = avg_ltv, fill = broad_class)) +
  geom_col(width = 0.5) +
  geom_text(aes(label = dollar(avg_ltv, accuracy = 1)), vjust = -0.5, size = 5, fontface = "bold") +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = dollar, expand = expansion(mult = c(0, 0.15))) +
  labs(x = "", y = "Avg LTV", fill = "Customer Type",
       subtitle = "Average total spend per customer (2023-2025)") +
  theme_buyer
```

# Classification Confidence

Not all orders can be definitively classified. Orders with no signal from any data source are labeled "Residential (assumed)" to distinguish them from confirmed residential customers.

```{r plot-confidence, fig.height=5}
certainty_long <- orders_merged %>%
  count(order_year, display_class) %>%
  group_by(order_year) %>%
  mutate(pct = round(n / sum(n) * 100, 1)) %>%
  ungroup()

certainty_long %>%
  ggplot(aes(x = factor(order_year), y = n, fill = display_class)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = paste0(pct, "%")),
            position = position_stack(vjust = 0.5), size = 4, color = "white",
            fontface = "bold") +
  scale_fill_manual(values = colors_detail) +
  scale_y_continuous(labels = comma) +
  labs(x = "Year", y = "Order Count", fill = "",
       subtitle = "Shows assumed-residential orders (no signals) separately") +
  theme_buyer
```

```{r certainty-table}
cert_tbl <- certainty_summary %>%
  select(Year = order_year, Total = total, Professional = classified_pro,
         Residential = classified_res, `No Signal` = no_signal,
         `% No Signal` = pct_no_signal, `Matched to CRM` = matched_to_zoho,
         `% Matched` = pct_matched)

kable(cert_tbl, align = "lrrrrrrr")
```

# Data Integrity: Stripe Cross-Reference

Stripe serves as the authoritative payment source. The BigCommerce export captures a subset of total orders. This section quantifies the gap.

```{r stripe-integrity-table}
stripe_integrity <- tibble(
  Metric = c(
    "Stripe total revenue (all time)",
    "Stripe total transactions",
    "Stripe unique customers",
    "Customers in both BC & Stripe",
    "BigCommerce-only customers",
    "Stripe-only customers (not in BC)",
    "Stripe-only revenue",
    "BC capture rate vs Stripe (matched customers)"
  ),
  Value = c(
    dollar(sum(stripe_lookup$stripe_total_spend, na.rm = TRUE)),
    comma(sum(stripe_lookup$stripe_payment_count, na.rm = TRUE)),
    comma(nrow(stripe_lookup)),
    comma(length(both)),
    comma(length(bc_only)),
    comma(length(stripe_only)),
    dollar(sum(stripe_only_classified$stripe_total_spend, na.rm = TRUE)),
    paste0(revenue_comparison$bc_capture_rate, "%")
  )
)

kable(stripe_integrity, align = "lr")
```

# Methodology

## Data Sources

| Source | Records | Purpose |
|--------|---------|---------|
| BigCommerce Orders | `r comma(nrow(bc_orders))` | Order-level transactions with product, shipping, and customer details |
| Zoho CRM Contacts | `r comma(nrow(zoho_contacts))` | Customer classification fields: type, trade program, business info |
| Stripe Customers | `r comma(nrow(stripe_customers))` | Authoritative payment data for revenue cross-validation |

## Classification Logic

Customers are classified as **Professional** if they exhibit any **strong signal** or two or more **weak signals**:

**Strong signals** (any one is sufficient):

- CRM Customer Type = commercial, professional, contractor, builder, designer, etc.
- CRM Business Type is set (e.g., general contractor, cabinet shop, property management)
- CRM Contact Type = professional, commercial, contractor, trade
- Active trade program status or expressed trade program interest
- Business ID or Business Entity on file
- Tax exempt status

**Weak signals** (require two together):

- Company name on file (after filtering junk entries like personal names, "home", "yes", "kitchen")
- Non-personal email domain (i.e., not Gmail, Yahoo, Outlook, etc.)

**Residential**: Explicitly tagged as homeowner/residential in CRM with no professional signals.

**Unknown (assumed Residential)**: No signals in any direction. These are conservatively grouped with Residential in the analysis but tracked separately for transparency.

## Merge Strategy

Records are matched across systems primarily by **email address** (lowercased, trimmed). For BigCommerce orders not matched to Zoho, the shipping company name and BigCommerce customer group provide fallback classification signals.

---

*Report generated `r format(Sys.time(), '%B %d, %Y at %I:%M %p')`*
