---
title: "Customer Segmentation Analysis"
subtitle: "Residential vs. Professional Order Breakdown"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
    fig_width: 10
    fig_height: 6
    css: !expr NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE,
  fig.align = "center", out.width = "100%"
)

library(dplyr)
library(ggplot2)
library(readr)
library(stringr)
library(tidyr)
library(lubridate)
library(scales)
library(gridExtra)
library(knitr)
```

```{r load-data}
bc_orders <- read_csv("orders-2026-03-25.csv", show_col_types = FALSE)
zoho_contacts <- read_csv("Contacts_2026_03_25.csv", show_col_types = FALSE)
zoho_accounts <- read_csv("Accounts_2025_03_25.csv", show_col_types = FALSE)
stripe_customers <- read_csv("stripe_unified_customers.csv", show_col_types = FALSE)
```

```{r prep-bigcommerce}
bc_clean <- bc_orders %>%
  mutate(
    order_date = mdy(`Order Date`),
    order_year = year(order_date),
    order_total = as.numeric(gsub("[^0-9.]", "", `Order Total (inc tax)`)),
    customer_email = tolower(trimws(`Customer Email`)),
    billing_email = tolower(trimws(`Billing Email`)),
    shipping_company = tolower(trimws(`Shipping Company`)),
    billing_company = tolower(trimws(`Billing Company`)),
    customer_group = tolower(trimws(`Customer Group Name`)),
    customer_name = trimws(`Customer Name`),
    billing_name = trimws(`Billing Name`),
    shipping_name = trimws(`Shipping Name`)
  ) %>%
  filter(order_year %in% c(2023, 2024, 2025)) %>%
  mutate(
    match_email = case_when(
      !is.na(customer_email) & customer_email != "" ~ customer_email,
      !is.na(billing_email) & billing_email != ""   ~ billing_email,
      TRUE ~ NA_character_
    )
  )
```

```{r prep-zoho}
zoho_clean <- zoho_contacts %>%
  mutate(
    zoho_email = tolower(trimws(Email)),
    zoho_customer_type = tolower(trimws(`Customer Type`)),
    zoho_business_type = tolower(trimws(`Business Type`)),
    zoho_contact_type = tolower(trimws(`Contact Type`)),
    zoho_lead_source = tolower(trimws(`Lead Source`)),
    zoho_trade_status = tolower(trimws(`Trade Program Status`)),
    zoho_trade_interest = tolower(trimws(`Trade Program Interest`)),
    zoho_trade_program = tolower(trimws(`Trade Program`)),
    zoho_professional_type = tolower(trimws(ifelse(
      "professionalType" %in% names(.), `professionalType`, NA_character_
    ))),
    zoho_customer_type_meta = tolower(trimws(ifelse(
      "customerType" %in% names(.), `customerType`, NA_character_
    ))),
    zoho_trade_interest_meta = tolower(trimws(ifelse(
      "tradeProgramInterest" %in% names(.), `tradeProgramInterest`, NA_character_
    ))),
    zoho_pro_project_type = tolower(trimws(ifelse(
      "proProjectType" %in% names(.), `proProjectType`, NA_character_
    ))),
    zoho_projects_per_year = tolower(trimws(`Projects per Year`)),
    zoho_disaster_recovery = tolower(trimws(`Disaster Recovery?`)),
    zoho_business_id = trimws(`Business ID`),
    zoho_business_entity = trimws(`Business Entity`),
    zoho_tax_exempt = tolower(trimws(`Tax Exempt?`)),
    zoho_company = tolower(trimws(`Account Name`)),
    zoho_first_name = trimws(`First Name`),
    zoho_last_name = trimws(`Last Name`),
    zoho_full_name = trimws(paste(zoho_first_name, zoho_last_name))
  )
```

```{r classify-zoho}
personal_email_domains <- c(
  "gmail.com", "yahoo.com", "hotmail.com", "outlook.com", "aol.com",
  "icloud.com", "me.com", "mac.com", "live.com", "msn.com",
  "comcast.net", "att.net", "verizon.net", "sbcglobal.net", "cox.net",
  "charter.net", "earthlink.net", "optonline.net", "frontier.com",
  "windstream.net", "centurylink.net", "embarqmail.com", "suddenlink.net",
  "mail.com", "email.com", "ymail.com", "rocketmail.com", "protonmail.com",
  "zoho.com", "fastmail.com", "hushmail.com", "inbox.com", "gmx.com"
)

company_junk <- c(
  "", "n/a", "na", "none", "no", "self", "retired", "home", "homeowner",
  "yes", "kitchen", "bath", "bathroom", "bathroom remodel", "cabinet doors",
  "stock cabinets", "custom cabinets", "cabinets", "google", "bigcommerce",
  "reflectiz bigcommerce", "facebook", "instagram"
)

zoho_classified <- zoho_clean %>%
  mutate(
    email_domain = str_extract(zoho_email, "(?<=@)[^@]+$"),
    has_business_email = !is.na(email_domain) & !(email_domain %in% personal_email_domains),
    sig_customer_type = zoho_customer_type %in% c(
      "professional", "commercial", "contractor", "builder", "designer",
      "architect", "trade", "dealer", "wholesale", "business"
    ),
    sig_business_type = !is.na(zoho_business_type) & zoho_business_type != "" &
      zoho_business_type != "homeowner" & zoho_business_type != "residential",
    sig_contact_type = zoho_contact_type %in% c(
      "professional", "commercial", "contractor", "trade", "dealer", "business"
    ),
    sig_trade_status = !is.na(zoho_trade_status) & zoho_trade_status != "" &
      zoho_trade_status != "none" & zoho_trade_status != "n/a",
    sig_trade_interest = !is.na(zoho_trade_interest) & zoho_trade_interest != "" &
      zoho_trade_interest != "no" & zoho_trade_interest != "none" &
      zoho_trade_interest != "n/a",
    sig_trade_program = !is.na(zoho_trade_program) & zoho_trade_program == "true",
    sig_professional_type = !is.na(zoho_professional_type) &
      zoho_professional_type != "" & zoho_professional_type != "homeowner",
    sig_business_id = !is.na(zoho_business_id) & zoho_business_id != "",
    sig_business_entity = !is.na(zoho_business_entity) & zoho_business_entity != "",
    sig_tax_exempt = !is.na(zoho_tax_exempt) & zoho_tax_exempt != "",
    sig_customer_type_meta = !is.na(zoho_customer_type_meta) &
      zoho_customer_type_meta %in% c("professional", "both"),
    sig_trade_interest_meta = !is.na(zoho_trade_interest_meta) &
      zoho_trade_interest_meta != "",
    sig_pro_project_type = !is.na(zoho_pro_project_type) & zoho_pro_project_type != "",
    sig_projects_per_year = !is.na(zoho_projects_per_year) & zoho_projects_per_year != "",
    sig_disaster_recovery = !is.na(zoho_disaster_recovery) &
      zoho_disaster_recovery != "" & zoho_disaster_recovery != "no",
    sig_company_raw = !is.na(zoho_company) &
      !(zoho_company %in% company_junk) &
      !(zoho_company == tolower(paste(zoho_first_name, zoho_last_name))) &
      !(zoho_company == tolower(zoho_last_name)),
    sig_email_raw = has_business_email,
    sig_residential = (zoho_customer_type %in% c("homeowner", "residential") |
      zoho_business_type %in% c("homeowner", "residential") |
      zoho_contact_type %in% c("homeowner", "residential") |
      zoho_customer_type_meta == "homeowner"),
    strong_signal_count = sig_customer_type + sig_business_type + sig_contact_type +
      sig_trade_status + sig_trade_interest + sig_trade_program +
      sig_professional_type + sig_business_id + sig_business_entity +
      sig_tax_exempt + sig_customer_type_meta + sig_trade_interest_meta +
      sig_pro_project_type + sig_projects_per_year + sig_disaster_recovery,
    weak_signal_count = sig_company_raw + sig_email_raw,
    pro_signal_count = strong_signal_count + weak_signal_count,
    is_professional = (strong_signal_count >= 1) | (weak_signal_count >= 2),
    customer_class = case_when(
      is_professional & !sig_residential ~ "Professional",
      is_professional & sig_residential  ~ "Professional",
      sig_residential                    ~ "Residential",
      TRUE                               ~ "Unknown"
    ),
    classification_confidence = case_when(
      strong_signal_count >= 2 ~ "High",
      strong_signal_count == 1 ~ "Medium",
      weak_signal_count >= 2   ~ "Low",
      sig_residential          ~ "Medium",
      TRUE                     ~ "No Signal"
    )
  )

# One row per email for lookups
zoho_lookup <- zoho_classified %>%
  filter(!is.na(zoho_email) & zoho_email != "") %>%
  group_by(zoho_email) %>%
  slice_max(pro_signal_count, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  select(zoho_email, customer_class, classification_confidence, pro_signal_count,
         zoho_company, zoho_customer_type, zoho_business_type, zoho_trade_status,
         starts_with("sig_"))
```

```{r accounts-and-address-signals}
# Zoho Accounts: additional classification source
acct_classified <- zoho_accounts %>%
  mutate(
    acct_email = tolower(trimws(ifelse("Email 1" %in% names(.), `Email 1`, NA_character_))),
    acct_customer_type = tolower(trimws(`Customer Type`)),
    acct_business_type = tolower(trimws(`Business Type`)),
    acct_contact_type = tolower(trimws(`Contact Type`)),
    acct_trade_interest = tolower(trimws(`Trade Program Interest`)),
    acct_trade_program = tolower(trimws(`Trade Program`)),
    acct_projects_per_year = tolower(trimws(`Projects per Year`)),
    acct_disaster_recovery = tolower(trimws(`Disaster Recovery?`)),
    acct_account_type = tolower(trimws(`Account Type`)),
    acct_industry = tolower(trimws(Industry))
  ) %>%
  mutate(
    acct_is_pro = acct_customer_type %in% c("professional","commercial","contractor","builder",
      "designer","architect","trade","dealer","wholesale","business") |
      (!is.na(acct_business_type) & acct_business_type != "" &
       !acct_business_type %in% c("homeowner","residential")) |
      acct_contact_type %in% c("professional","commercial","contractor","trade","dealer","business") |
      (!is.na(acct_trade_interest) & acct_trade_interest != "" &
       !acct_trade_interest %in% c("no","none","n/a")) |
      (!is.na(acct_trade_program) & acct_trade_program == "true") |
      (!is.na(acct_projects_per_year) & acct_projects_per_year != "") |
      (!is.na(acct_disaster_recovery) & acct_disaster_recovery != "" & acct_disaster_recovery != "no") |
      (!is.na(acct_industry) & acct_industry != "") |
      (!is.na(acct_account_type) & acct_account_type != "" &
       !acct_account_type %in% c("customer","other",""))
  )

acct_lookup <- acct_classified %>%
  filter(!is.na(acct_email) & acct_email != "" & acct_is_pro) %>%
  distinct(acct_email) %>% mutate(acct_is_professional = TRUE)

# BigCommerce: different shipping vs billing name+address = professional
bc_address_signal <- bc_clean %>%
  filter(!is.na(match_email)) %>%
  mutate(
    ship_name = tolower(trimws(`Shipping Name`)),
    bill_name = tolower(trimws(`Billing Name`)),
    ship_addr = tolower(trimws(paste(`Shipping Street 1`, `Shipping Suburb`,
                                      `Shipping State`, `Shipping Zip`))),
    bill_addr = tolower(trimws(paste(`Billing Street 1`, `Billing Suburb`,
                                      `Billing State`, `Billing Zip`))),
    diff_name_and_addr = !is.na(ship_name) & !is.na(bill_name) & ship_name != "" &
      bill_name != "" & ship_name != bill_name &
      !is.na(ship_addr) & !is.na(bill_addr) & ship_addr != bill_addr
  ) %>%
  group_by(match_email) %>%
  summarise(has_diff_ship_bill = any(diff_name_and_addr, na.rm = TRUE), .groups = "drop") %>%
  filter(has_diff_ship_bill)
```

```{r stripe-master}
# ==========================================================================
# STRIPE AS AUTHORITY: Build the master customer list from Stripe
# ==========================================================================

stripe_clean <- stripe_customers %>%
  mutate(
    stripe_email = tolower(trimws(Email)),
    stripe_name = trimws(Name),
    stripe_total_spend = as.numeric(gsub("[^0-9.]", "", `Total Spend`)),
    stripe_payment_count = as.numeric(`Payment Count`),
    stripe_avg_order = as.numeric(gsub("[^0-9.]", "", `Average Order`)),
    stripe_refunded = as.numeric(gsub("[^0-9.]", "", `Refunded Volume`)),
    stripe_created = ymd_hms(`Created (UTC)`, quiet = TRUE)
  ) %>%
  filter(!is.na(stripe_email) & stripe_email != "")

# Consolidate to one row per email (Stripe can have duplicates)
stripe_deduped <- stripe_clean %>%
  group_by(stripe_email) %>%
  summarise(
    stripe_name = first(na.omit(stripe_name)),
    total_spend = sum(stripe_total_spend, na.rm = TRUE),
    total_orders = sum(stripe_payment_count, na.rm = TRUE),
    avg_order = ifelse(sum(stripe_payment_count, na.rm = TRUE) > 0,
                       sum(stripe_total_spend, na.rm = TRUE) / sum(stripe_payment_count, na.rm = TRUE),
                       0),
    total_refunded = sum(stripe_refunded, na.rm = TRUE),
    first_seen = min(stripe_created, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  filter(total_spend > 0) %>%
  mutate(first_year = year(first_seen))

# Filter to customers active in 2023-2025
bc_active_emails <- bc_clean %>%
  filter(!is.na(match_email)) %>% distinct(match_email) %>% pull()

customer_master <- stripe_deduped %>%
  filter(
    first_year >= 2023 |                   # Created during period
    stripe_email %in% bc_active_emails     # Has BC order in 2023-2025
  )

# Classify from Zoho
customer_master <- customer_master %>%
  left_join(zoho_lookup %>% select(zoho_email, customer_class, classification_confidence,
                                    pro_signal_count),
            by = c("stripe_email" = "zoho_email"))

# Enrich from BigCommerce for unmatched
bc_company_lookup <- bc_clean %>%
  filter(!is.na(match_email)) %>%
  group_by(match_email) %>%
  summarise(
    bc_shipping_company = first(na.omit(shipping_company)),
    bc_billing_company = first(na.omit(billing_company)),
    bc_customer_group = first(na.omit(customer_group)),
    .groups = "drop"
  ) %>%
  mutate(
    bc_has_shipping_co = !is.na(bc_shipping_company) & bc_shipping_company != "" &
      !bc_shipping_company %in% c("n/a", "na", "none", "-"),
    bc_has_billing_co = !is.na(bc_billing_company) & bc_billing_company != "" &
      !bc_billing_company %in% c("n/a", "na", "none", "-"),
    bc_has_company = bc_has_shipping_co | bc_has_billing_co,
    bc_group_pro = bc_customer_group %in% c(
      "professional", "commercial", "trade", "wholesale", "dealer",
      "contractor", "builder", "business"
    )
  )

customer_master <- customer_master %>%
  left_join(bc_company_lookup, by = c("stripe_email" = "match_email")) %>%
  left_join(acct_lookup, by = c("stripe_email" = "acct_email")) %>%
  left_join(bc_address_signal, by = c("stripe_email" = "match_email")) %>%
  mutate(
    acct_is_professional = ifelse(is.na(acct_is_professional), FALSE, acct_is_professional),
    has_diff_ship_bill = ifelse(is.na(has_diff_ship_bill), FALSE, has_diff_ship_bill),
    # Professional always wins
    final_class = case_when(
      customer_class == "Professional"       ~ "Professional",
      acct_is_professional                   ~ "Professional",
      bc_has_company | bc_group_pro          ~ "Professional",
      has_diff_ship_bill                     ~ "Professional",
      customer_class == "Residential"        ~ "Residential",
      TRUE                                   ~ "Unknown"
    ),
    display_class = case_when(
      final_class == "Professional" ~ "Professional",
      final_class == "Residential"  ~ "Residential",
      TRUE                          ~ "Residential (assumed)"
    ),
    broad_class = ifelse(final_class == "Professional", "Professional", "Residential"),
    is_repeat = total_orders > 1
  )
```

```{r bc-yearly-data}
# BigCommerce order-level data for yearly trend analysis
orders_merged <- bc_clean %>%
  left_join(zoho_lookup %>% select(zoho_email, customer_class),
            by = c("match_email" = "zoho_email")) %>%
  left_join(bc_company_lookup %>% select(match_email, bc_has_company, bc_group_pro),
            by = c("match_email" = "match_email")) %>%
  left_join(acct_lookup, by = c("match_email" = "acct_email")) %>%
  left_join(bc_address_signal, by = c("match_email" = "match_email")) %>%
  mutate(
    acct_is_professional = ifelse(is.na(acct_is_professional), FALSE, acct_is_professional),
    has_diff_ship_bill = ifelse(is.na(has_diff_ship_bill), FALSE, has_diff_ship_bill),
    # Professional always wins
    final_class = case_when(
      customer_class == "Professional"       ~ "Professional",
      acct_is_professional                   ~ "Professional",
      bc_has_company | bc_group_pro          ~ "Professional",
      has_diff_ship_bill                     ~ "Professional",
      customer_class == "Residential"        ~ "Residential",
      TRUE                                   ~ "Unknown"
    ),
    display_class = case_when(
      final_class == "Professional" ~ "Professional",
      final_class == "Residential"  ~ "Residential",
      TRUE                          ~ "Residential (assumed)"
    ),
    broad_class = ifelse(final_class == "Professional", "Professional", "Residential")
  )

# Yearly summary from BC (for trend charts)
yearly_summary <- orders_merged %>%
  group_by(order_year, broad_class) %>%
  summarise(
    order_count = n(),
    total_revenue = sum(order_total, na.rm = TRUE),
    avg_order_size = mean(order_total, na.rm = TRUE),
    median_order_size = median(order_total, na.rm = TRUE),
    unique_customers = n_distinct(match_email, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  group_by(order_year) %>%
  mutate(
    pct_orders = round(order_count / sum(order_count) * 100, 1),
    pct_revenue = round(total_revenue / sum(total_revenue) * 100, 1)
  ) %>%
  ungroup()

# Repeat by year from BC
repeat_by_year <- orders_merged %>%
  filter(!is.na(match_email)) %>%
  arrange(match_email, order_date) %>%
  group_by(match_email) %>%
  mutate(cumulative_order_num = row_number(), is_repeat_order = cumulative_order_num > 1) %>%
  ungroup() %>%
  group_by(order_year, broad_class) %>%
  summarise(total_orders = n(), repeat_orders = sum(is_repeat_order),
            repeat_order_rate = round(repeat_orders / total_orders * 100, 1),
            .groups = "drop")
```

```{r compute-summaries}
# --- Stripe-authoritative totals ---
total_customers <- nrow(customer_master)
total_revenue <- sum(customer_master$total_spend, na.rm = TRUE)
total_orders <- sum(customer_master$total_orders, na.rm = TRUE)
no_signal_pct <- round(sum(customer_master$final_class == "Unknown") / total_customers * 100, 1)

# Summary by type (from Stripe)
type_summary <- customer_master %>%
  group_by(broad_class) %>%
  summarise(
    customers = n(),
    revenue = sum(total_spend, na.rm = TRUE),
    orders = sum(total_orders, na.rm = TRUE),
    avg_order = round(sum(total_spend, na.rm = TRUE) / sum(total_orders, na.rm = TRUE), 2),
    avg_ltv = round(mean(total_spend, na.rm = TRUE), 2),
    median_ltv = round(median(total_spend, na.rm = TRUE), 2),
    repeat_customers = sum(is_repeat),
    repeat_rate = round(sum(is_repeat) / n() * 100, 1),
    avg_orders_per_cust = round(mean(total_orders, na.rm = TRUE), 2),
    .groups = "drop"
  ) %>%
  mutate(
    pct_customers = round(customers / sum(customers) * 100, 1),
    pct_revenue = round(revenue / sum(revenue) * 100, 1),
    pct_orders = round(orders / sum(orders) * 100, 1)
  )

# Certainty from Stripe master
certainty_stripe <- customer_master %>%
  count(display_class) %>%
  mutate(pct = round(n / sum(n) * 100, 1))
```

```{r theme-setup}
theme_buyer <- theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", size = 15),
    plot.subtitle = element_text(color = "gray40", size = 11),
    legend.position = "bottom",
    panel.grid.minor = element_blank()
  )

colors_class <- c("Professional" = "#2C5F8A", "Residential" = "#E8894A")
colors_detail <- c("Professional" = "#2C5F8A", "Residential" = "#E8894A",
                    "Residential (assumed)" = "#F5C285")
```

# Executive Summary

This report analyzes **`r comma(total_customers)`** paying customers representing **`r dollar(total_revenue)`** in total revenue across **`r comma(total_orders)`** orders. Revenue and customer counts are sourced from **Stripe** (authoritative payment system). Customer classification uses signals from **Zoho CRM** and **BigCommerce**.

```{r exec-summary-table}
exec_tbl <- type_summary %>%
  transmute(
    `Customer Type` = broad_class,
    Customers = comma(customers),
    `% Customers` = paste0(pct_customers, "%"),
    Orders = comma(orders),
    `% Orders` = paste0(pct_orders, "%"),
    Revenue = dollar(revenue),
    `% Revenue` = paste0(pct_revenue, "%"),
    `Avg Order` = dollar(avg_order),
    `Avg LTV` = dollar(avg_ltv)
  )

kable(exec_tbl, align = "lrrrrrrrr")
```

> **Classification certainty:** `r no_signal_pct`% of customers had no signal indicating either type and are assumed Residential. These are tracked separately in the confidence section below.

---

# Customer Composition {.tabset}

## By Customer Count

```{r plot-cust-count, fig.height=5, fig.width=8}
type_summary %>%
  ggplot(aes(x = broad_class, y = customers, fill = broad_class)) +
  geom_col(width = 0.5) +
  geom_text(aes(label = paste0(comma(customers), "\n(", pct_customers, "%)")),
            vjust = -0.3, size = 4.5, fontface = "bold") +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = comma, expand = expansion(mult = c(0, 0.2))) +
  labs(x = "", y = "Customers", fill = "Customer Type",
       title = "Customers by Type",
       subtitle = "Based on Stripe payment records (paying customers only)") +
  theme_buyer
```

## By Revenue

```{r plot-rev-split, fig.height=5, fig.width=8}
type_summary %>%
  ggplot(aes(x = broad_class, y = revenue, fill = broad_class)) +
  geom_col(width = 0.5) +
  geom_text(aes(label = paste0(dollar(revenue, accuracy = 1), "\n(", pct_revenue, "%)")),
            vjust = -0.3, size = 4.5, fontface = "bold") +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = dollar, expand = expansion(mult = c(0, 0.2))) +
  labs(x = "", y = "Revenue", fill = "Customer Type",
       title = "Revenue by Customer Type",
       subtitle = "Total lifetime revenue from Stripe") +
  theme_buyer
```

## By Order Count

```{r plot-order-split, fig.height=5, fig.width=8}
type_summary %>%
  ggplot(aes(x = broad_class, y = orders, fill = broad_class)) +
  geom_col(width = 0.5) +
  geom_text(aes(label = paste0(comma(orders), "\n(", pct_orders, "%)")),
            vjust = -0.3, size = 4.5, fontface = "bold") +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = comma, expand = expansion(mult = c(0, 0.2))) +
  labs(x = "", y = "Orders", fill = "Customer Type",
       title = "Orders by Customer Type",
       subtitle = "Total order count from Stripe") +
  theme_buyer
```

# Average Order Size & Customer LTV

```{r plot-avg-ltv, fig.height=5}
ltv_data <- type_summary %>%
  select(broad_class, `Avg Order Size` = avg_order, `Avg Customer LTV` = avg_ltv,
         `Median Customer LTV` = median_ltv) %>%
  pivot_longer(-broad_class, names_to = "metric", values_to = "value") %>%
  mutate(metric = factor(metric, levels = c("Avg Order Size", "Avg Customer LTV", "Median Customer LTV")))

ltv_data %>%
  ggplot(aes(x = metric, y = value, fill = broad_class)) +
  geom_col(position = "dodge", width = 0.7) +
  geom_text(aes(label = dollar(value, accuracy = 1)),
            position = position_dodge(width = 0.7), vjust = -0.5, size = 4) +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = dollar, expand = expansion(mult = c(0, 0.15))) +
  labs(x = "", y = "", fill = "Customer Type",
       title = "Order Size & Lifetime Value by Customer Type",
       subtitle = "From Stripe payment data") +
  theme_buyer
```

# Repeat Customer Behavior

```{r plot-repeat, fig.height=5}
repeat_data <- type_summary %>%
  select(broad_class, repeat_rate, avg_orders_per_cust) %>%
  pivot_longer(-broad_class, names_to = "metric", values_to = "value") %>%
  mutate(metric = recode(metric,
    "repeat_rate" = "Repeat Rate (%)",
    "avg_orders_per_cust" = "Avg Orders per Customer"
  ))

gridExtra::grid.arrange(
  # Repeat rate
  type_summary %>%
    ggplot(aes(x = broad_class, y = repeat_rate, fill = broad_class)) +
    geom_col(width = 0.5) +
    geom_text(aes(label = paste0(repeat_rate, "%")), vjust = -0.5, size = 5, fontface = "bold") +
    scale_fill_manual(values = colors_class) +
    scale_y_continuous(labels = function(x) paste0(x, "%"), expand = expansion(mult = c(0, 0.2))) +
    labs(x = "", y = "Repeat Rate", fill = "Customer Type",
         title = "Repeat Customer Rate", subtitle = "Customers with 2+ orders") +
    theme_buyer,

  # Avg orders per customer
  type_summary %>%
    ggplot(aes(x = broad_class, y = avg_orders_per_cust, fill = broad_class)) +
    geom_col(width = 0.5) +
    geom_text(aes(label = sprintf("%.1f", avg_orders_per_cust)), vjust = -0.5, size = 5, fontface = "bold") +
    scale_fill_manual(values = colors_class) +
    scale_y_continuous(expand = expansion(mult = c(0, 0.2))) +
    labs(x = "", y = "Avg Orders", fill = "Customer Type",
         title = "Orders per Customer", subtitle = "Average from Stripe") +
    theme_buyer,

  ncol = 2
)
```

```{r repeat-table}
repeat_tbl <- type_summary %>%
  transmute(
    Type = broad_class,
    Customers = comma(customers),
    `Repeat Customers` = comma(repeat_customers),
    `Repeat Rate` = paste0(repeat_rate, "%"),
    `Avg Orders/Customer` = avg_orders_per_cust,
    `Avg LTV` = dollar(avg_ltv),
    `Median LTV` = dollar(median_ltv)
  )

kable(repeat_tbl, align = "lrrrrrr")
```

# Year-over-Year Trends

*Note: Yearly breakdowns use BigCommerce order data, which captures a subset of total Stripe transactions. These charts show directional trends rather than absolute totals.*

## Order Volume by Year

```{r plot-yearly-orders, fig.height=5}
yearly_summary %>%
  ggplot(aes(x = factor(order_year), y = order_count, fill = broad_class)) +
  geom_col(position = "dodge", width = 0.7) +
  geom_text(aes(label = comma(order_count)),
            position = position_dodge(width = 0.7), vjust = -0.5, size = 4) +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = comma, expand = expansion(mult = c(0, 0.15))) +
  labs(x = "Year", y = "Order Count", fill = "Customer Type",
       title = "Orders by Customer Type and Year",
       subtitle = "Source: BigCommerce (partial coverage)") +
  theme_buyer
```

## Revenue by Year

```{r plot-yearly-revenue, fig.height=5}
yearly_summary %>%
  ggplot(aes(x = factor(order_year), y = total_revenue, fill = broad_class)) +
  geom_col(position = "dodge", width = 0.7) +
  geom_text(aes(label = dollar(total_revenue, accuracy = 1)),
            position = position_dodge(width = 0.7), vjust = -0.5, size = 3.5) +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = dollar, expand = expansion(mult = c(0, 0.15))) +
  labs(x = "Year", y = "Revenue", fill = "Customer Type",
       title = "Revenue by Customer Type and Year",
       subtitle = "Source: BigCommerce (partial coverage)") +
  theme_buyer
```

## Revenue Share by Year

```{r plot-yearly-share, fig.height=5}
yearly_summary %>%
  ggplot(aes(x = factor(order_year), y = pct_revenue, fill = broad_class)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = paste0(pct_revenue, "%")),
            position = position_stack(vjust = 0.5), size = 5, color = "white",
            fontface = "bold") +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = function(x) paste0(x, "%")) +
  labs(x = "Year", y = "% of Revenue", fill = "Customer Type",
       title = "Revenue Share by Customer Type",
       subtitle = "Source: BigCommerce (partial coverage)") +
  theme_buyer
```

## Average Order Size by Year

```{r plot-yearly-avg, fig.height=5}
yearly_summary %>%
  ggplot(aes(x = factor(order_year), y = avg_order_size, fill = broad_class)) +
  geom_col(position = "dodge", width = 0.7) +
  geom_text(aes(label = dollar(avg_order_size, accuracy = 1)),
            position = position_dodge(width = 0.7), vjust = -0.5, size = 4) +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = dollar, expand = expansion(mult = c(0, 0.15))) +
  labs(x = "Year", y = "Avg Order Size", fill = "Customer Type",
       title = "Average Order Size by Year",
       subtitle = "Source: BigCommerce (partial coverage)") +
  theme_buyer
```

## Repeat Order Rate by Year

```{r plot-yearly-repeat, fig.height=5}
repeat_by_year %>%
  ggplot(aes(x = factor(order_year), y = repeat_order_rate, fill = broad_class)) +
  geom_col(position = "dodge", width = 0.7) +
  geom_text(aes(label = paste0(repeat_order_rate, "%")),
            position = position_dodge(width = 0.7), vjust = -0.5, size = 4) +
  scale_fill_manual(values = colors_class) +
  scale_y_continuous(labels = function(x) paste0(x, "%"),
                     expand = expansion(mult = c(0, 0.15))) +
  labs(x = "Year", y = "Repeat Order %", fill = "Customer Type",
       title = "Repeat Order Rate by Year",
       subtitle = "% of orders from returning customers (BigCommerce data)") +
  theme_buyer
```

```{r yearly-detail-table}
yearly_tbl <- yearly_summary %>%
  transmute(
    Year = order_year, Type = broad_class,
    Orders = comma(order_count), `% Orders` = paste0(pct_orders, "%"),
    Revenue = dollar(total_revenue), `% Rev` = paste0(pct_revenue, "%"),
    `Avg Order` = dollar(avg_order_size), `Median` = dollar(median_order_size),
    Customers = comma(unique_customers)
  )

kable(yearly_tbl, align = "llrrrrrrrr")
```

# Classification Confidence

```{r plot-confidence, fig.height=5, fig.width=8}
certainty_stripe %>%
  ggplot(aes(x = "", y = n, fill = display_class)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = paste0(display_class, "\n", comma(n), " (", pct, "%)")),
            position = position_stack(vjust = 0.5), size = 4, color = "white",
            fontface = "bold") +
  scale_fill_manual(values = colors_detail) +
  coord_flip() +
  labs(x = "", y = "Customers", fill = "",
       title = "Customer Classification Breakdown",
       subtitle = "Paying customers from Stripe, classified via CRM and BigCommerce signals") +
  theme_buyer +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
```

```{r certainty-table}
cert_tbl <- customer_master %>%
  group_by(Classification = display_class) %>%
  summarise(
    Customers = n(),
    Revenue = dollar(sum(total_spend, na.rm = TRUE)),
    Orders = comma(sum(total_orders, na.rm = TRUE)),
    `Avg LTV` = dollar(mean(total_spend, na.rm = TRUE)),
    .groups = "drop"
  ) %>%
  mutate(`% of Customers` = paste0(round(Customers / sum(Customers) * 100, 1), "%"))

kable(cert_tbl, align = "lrrrrr")
```

# Data Source Coverage

```{r coverage-table}
zoho_emails <- zoho_lookup %>% pull(zoho_email)
bc_emails <- bc_clean %>% filter(!is.na(match_email)) %>% distinct(match_email) %>% pull()
stripe_paying <- customer_master %>% pull(stripe_email)

coverage_tbl <- tibble(
  Metric = c(
    "Stripe paying customers (authority)",
    "Zoho CRM contacts",
    "BigCommerce orders (2023-2025)",
    "Stripe customers matched to Zoho",
    "Stripe customers matched to BigCommerce",
    "Stripe customers with ANY classification signal",
    "Stripe customers with no signal (assumed Residential)"
  ),
  Value = c(
    comma(length(stripe_paying)),
    comma(length(zoho_emails)),
    comma(nrow(bc_clean)),
    paste0(comma(sum(stripe_paying %in% zoho_emails)), " (",
           round(sum(stripe_paying %in% zoho_emails) / length(stripe_paying) * 100, 1), "%)"),
    paste0(comma(sum(stripe_paying %in% bc_emails)), " (",
           round(sum(stripe_paying %in% bc_emails) / length(stripe_paying) * 100, 1), "%)"),
    paste0(comma(sum(customer_master$final_class != "Unknown")), " (",
           round(sum(customer_master$final_class != "Unknown") / nrow(customer_master) * 100, 1), "%)"),
    paste0(comma(sum(customer_master$final_class == "Unknown")), " (",
           no_signal_pct, "%)")
  )
)

kable(coverage_tbl, align = "lr")
```

# Methodology

## Data Sources

| Source | Role | Records |
|--------|------|---------|
| **Stripe** | Authoritative payment data: customer totals, order counts, revenue | `r comma(nrow(stripe_customers))` raw records |
| **Zoho CRM** | Customer classification: type, trade program, business info | `r comma(nrow(zoho_contacts))` contacts |
| **BigCommerce** | Order-level detail with dates (partial coverage) for yearly trends | `r comma(nrow(bc_orders))` orders |

## Classification Logic

Customers are classified as **Professional** if they exhibit any **strong signal** or two or more **weak signals**:

**Strong signals** (any one is sufficient):

- CRM `Customer Type` = commercial, professional, contractor, builder, designer, etc.
- CRM `Business Type` is set (e.g., general contractor, cabinet shop, property management)
- CRM `Contact Type` = professional, commercial, contractor, trade
- CRM `Trade Program Status` is active
- CRM `Trade Program Interest` expressed
- CRM `Trade Program` = true (boolean field)
- CRM `professionalType` metadata (remodeler, home builder, handyman, cabinet shop, interior designer, etc.)
- CRM `customerType` metadata = professional or both
- CRM `tradeProgramInterest` metadata = yes
- CRM `proProjectType` metadata is set (indicates professional project context)
- CRM `Projects per Year` is set (indicates professional order volume)
- `Business ID` or `Business Entity` on file
- Tax exempt status

**Weak signals** (require two together):

- Company name on file (after filtering junk entries like personal names, "home", "yes", "kitchen")
- Non-personal email domain (i.e., not Gmail, Yahoo, Outlook, etc.)

**Residential**: Explicitly tagged as homeowner/residential in CRM `Customer Type`, `Business Type`, `Contact Type`, or `customerType` metadata, with no professional signals.

**Unknown (assumed Residential)**: No signals in any direction. Conservatively grouped with Residential but tracked separately for transparency.

## Scope

Only Stripe customers active in the 2023--2025 period are included. A customer is considered active if their Stripe account was created in 2023 or later, OR if they have a BigCommerce order dated within 2023--2025.

## Merge Strategy

All systems are joined on **email address** (lowercased, trimmed). Stripe serves as the master customer list (deduplicated by email, filtered to paying customers with activity in 2023--2025). Zoho CRM provides the primary classification via 14 strong signals and 2 weak signals. BigCommerce provides fallback signals (shipping company, customer group) and order-level date data for yearly trend analysis.

---

*Report generated `r format(Sys.time(), '%B %d, %Y at %I:%M %p')`*
